### 2017-03-22 paper/WASPAA2017_PaperTemplate_LaTeX/2017_WASPAA_PaperTemplate_LaTeX.tex
Initial commit.

% --------------------------------------------------------------------------
% Template for WASPAA-2017 paper; to be used with:
%          waspaa17.sty  - WASPAA 2017 LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
%
% --------------------------------------------------------------------------

\documentclass{article}
\usepackage{waspaa17,amsmath,graphicx,url,times}
%\usepackage{waspaa17,amssymb,amsmath,graphicx,times,url}
\usepackage{color}

% Example definitions.
% --------------------
\def\defeqn{\stackrel{\triangle}{=}}
\newcommand{\symvec}[1]{{\mbox{\boldmath $#1$}}}
\newcommand{\symmat}[1]{{\mbox{\boldmath $#1$}}}

% Title.
% --------------------
\title{AUTHOR GUIDELINES FOR WASPAA 2017 PROCEEDINGS MANUSCRIPTS}

%% Single addresses (uncomment and modify for single-address case).
%% --------------------
%\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
%\address{Author Affiliation(s)}
%%
%% For example:
%% ------------
%%\address{School\\
%%       Department\\
%%       Address}

% Two addresses
% --------------------
\twoauthors
  {John Doe\sthanks{Thanks to ABC agency for funding.}}
    {Fictional University\\
Computer Science Dept., 2133 Long Road\\
     Gotham, NY 10027, USA \\
     john@fictional.edu}
  {Maria Ortega\sthanks{Thanks to XYZ agency for funding.}}
    {University of the Imagination \\
     Big Engineering Building, 8765 Dream Blvd. \\
     New Chicago, IL 60626, USA \\
     maria@imagination.edu}

%% Many authors with many addresses
%% --------------------
%\name{John Doe,$^{1}$\sthanks{Thanks to ABC agency for funding.}
%      Maria Ortega,$^{2}$\sthanks{Thanks to XYZ agency for funding.}
%      Third Author,$^{3}$ \sthanks{Also many thanks.}
%      Fourth Author$^{2}$}
%\address{$^1$ Fictional University, Computer Science Dept., 2133 Long Road, Gotham, NY 10027, USA\\ john@fictional.edu\\              
%         $^2$ University of the Imagination, Big Engineering Building, 8765 Dream Blvd., New Chicago, IL 60626, USA\\
%          maria@imagination.edu, fourthAuthor@imagination.edu\\
%         $^3$ Important Laboratory, 123 Street, City, Country, thirdAuthor@test.edu\\       
%}

\begin{document}

\ninept
\maketitle

\begin{sloppy}

\begin{abstract}
  In order to help authors prepare their manuscripts for 
  submission to WASPAA 2017 and generate IEEE Xplore-compatible 
  PDFs, we compile a list of guidelines and put together two
  templates for users of both \LaTeX\ and Microsoft Word, which
  can be downloaded from the workshop website at \cite{waspaa17web}.
  These guidelines and templates are modified from those for 
  ICASSP and past WASPAA workshops, so an experienced author who 
  has published something in these conferences/workshops will 
  find it easy to follow the guidelines and use the templates.
\end{abstract}

\begin{keywords}
One, two, three, four, five
\end{keywords}

\section{Introduction}
\label{sec:intro}

The guidelines given below, including complete descriptions of 
the fonts, spacing, and related information for producing your 
proceedings manuscripts, are critical to produce the WASPAA 2017 
proceedings with a more uniform look and IEEE Xplore-compatible PDFs.

\section{Formatting your paper}
\label{sec:format}

All manuscripts must be submitted electronically as PDF files. 
All manuscripts must be formatted for white US letter paper 
(8.5 $\times$ 11 inches). Please do {\bf not} use A4-size papers. 
All printed material, including text, illustrations, and charts, 
must be kept within a print area of 7.0 inches (178 mm) wide 
by 8.9 inches (226 mm) high. Do not write or print anything outside 
the print area. The top margin must be 1 inch (25 mm), except for 
the title page, and the left margin must be 0.75 inch (19 mm).  
All {\it text} must be in a two-column format. Columns are to be 
3.29 inches (83.5 mm) wide, with a 0.31 inch (8 mm) space between 
them. Text must be fully justified.

\section{PDF EXPRESS}
\label{sec:PDF_express}

Accepted papers must pass IEEE PDF Express $^{\text{TM}}$ format 
verification prior to publication.  Format verification details will be 
announced with paper acceptance notification.

\section{COPYRIGHT FORMS}
\label{sec:copyright}

You must submit a fully completed, signed IEEE 
copyright release form after your manuscript is
selected for presentation on the workshop.
We {\bf must} have this form before your paper can be
published in the proceedings. The copyright form is 
available as a Word file, a PDF file, and an HTML file
at \cite{ieeecopyright}.
%\url{http://www.ieee.org/web/publications/rights/copyrightmain.html}. 
Copyright form submission details will be announced with paper acceptance notification.

\section{NUMBER OF PAGES}
\label{sec:pagelimit}

You are allowed a total of 5 pages for your document. Up to 4 pages may 
contain technical content, figures, and references, while the 5th page 
may contain only references. This is the max-imum number of pages that 
will be accepted, including all figures, tables, and references. Any 
documents that exceed the 5-page limit will be rejected. Any documents 
with a 5th page containing anything other than references will be rejected.

\section{PAGE TITLE SECTION}
\label{sec:pagestyle}

The paper title (on the first page) should begin 0.98 inches 
(25 mm) from the top edge of the page, centered, completely 
capitalized, and in Times 14-point, boldface type.  
The authors' name(s) and affiliation(s) appear below the title
in capital and lower case letters.  Papers with multiple authors 
and affiliations may require two or more lines for this information.

\section{TYPE-STYLE AND FONTS}
\label{sec:typestyle}

To achieve the best rendering both in the proceedings and 
from the CD-ROM, we strongly encourage you to use Times-Roman 
font. In addition, this will give the proceedings a more uniform 
look. Use a font that is no smaller than nine point type 
throughout the paper, including figure captions.

In nine point type font, capital letters are 2 mm high.  
{\bf If you use the smallest point size, there should be 
no more than 3.2 lines/cm (8 lines/inch) vertically.}  
This is a minimum spacing; 2.75 lines/cm (7 lines/inch) 
will make the paper much more readable. Larger type sizes 
require correspondingly larger vertical spacing. Please do 
not double-space your paper. True-Type 1 fonts are preferred.

The first paragraph in each section should not be indented, 
but all the following paragraphs within the section should 
be indented as these paragraphs demonstrate.

\section{MAJOR HEADINGS}
\label{sec:majhead}

Major headings, for example, ``1. Introduction'', should 
appear in all capital letters, bold face if possible, 
centered in the column, with one blank line before, 
and one blank line after. Use a period (``.'') after 
the heading number, not a colon.

\subsection{Subheadings}
\label{ssec:subhead}

Subheadings should appear in lower case (initial word 
capitalized) in boldface. They should start at the left 
margin on a separate line.

\subsubsection{Sub-subheadings}
\label{sssec:subsubhead}

Sub-subheadings, as in this paragraph, are discouraged. 
However, if you must use them, they should appear in 
lower case (initial word capitalized) and start at the 
left margin on a separate line, with paragraph
text beginning on the following line. They should be 
in italics.

\section{Page Numbering, Header, and Footer}
\label{sec:page}

Please do {\bf not} paginate your paper. Page numbers, 
session numbers, and conference identification will be 
inserted when the paper is included in the proceedings.
In addition, please do {\bf not} change and remove
the header and footer.

\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
\label{sec:illust}

Illustrations must appear within the designated margins.  
They may span the two columns. If possible, position 
illustrations at the top of columns, rather than in 
the middle or at the bottom. Caption and number every 
illustration. All halftone illustrations must be clear 
black and white prints. Colors may be used, but they 
should be selected so as to be readable when printed 
on a black-only printer.

Since there are many ways, often incompatible, of 
including images (e.g., with experimental results) 
in a \LaTeX\ document, an example of how to do
this is presented in Fig.~\ref{fig:results}.

% Below is an example of how to insert images. 
% -------------------------------------------------------------------------
\begin{figure}[t]
  \centering
  \centerline{\includegraphics[width=\columnwidth]{fig1a}}
  \caption{Example of a figure with experimental results.}
  \label{fig:results}
\end{figure}

\section{Equations}
\label{sec:equations}

Equations should be placed on separate lines and consecutively
numbered with equation numbers in parentheses flush with the 
right margin, as illustrated in (\ref{eqn:wave_equation}) 
that gives the homogeneous acoustic wave equation in
Cartesian coordinates \cite{eWilliams1999},
\begin{equation}
  \label{eqn:wave_equation}
    \Delta^2p(x,y,z,t)-
    \displaystyle\frac{1}{c^2}\frac{\partial^2p(x,y,z,t)}{\partial t^2}=0,
\end{equation}
where $p(x,y,z,t)$ is an infinitesimal variation of acoustic 
pressure from its equilibrium value at position $(x,y,z)$ and 
time $t$, and where $c$ denotes the speed of sound.

Symbols in your equation should be defined before the equation 
appears or immediately following.  Use (1), not Eq. (1) or 
equation (1), except at the beginning of a sentence:  
``Equation (1) is ...''

\section{FOOTNOTES}
\label{sec:foot}

Use footnotes sparingly (or not at all!) and place them at 
the bottom of the column on the page on which they are 
referenced. Use Times 9-point type, single-spaced. To 
help your readers, avoid using footnotes altogether and
include necessary peripheral observations in the text 
(within parentheses, if you prefer, as in this sentence).

\section{REFERENCES}
\label{sec:ref}

List and number all bibliographical references at the end 
of the paper. The references should be numbered in order 
of appearance in the document. When referring to them in 
the text, type the corresponding reference number in 
square brackets as shown at the end of this sentence 
\cite{cJones2003}, \cite{aSmith2000}. For \LaTeX\ users, 
the use of the Bib\TeX\ style file IEEEtran.bst is 
recommended, which is included in the \LaTeX\ paper 
kit available from the workshop website \cite{waspaa17web}.

\section{ACKNOWLEDGMENT}
\label{sec:ack}

The preferred spelling of the word acknowledgment in 
America is without an ``e'' after the ``g.'' Try to avoid 
the stilted expression, ``One of us (R. B. G.) thanks ...''
Instead, try ``R.B.G.\ thanks ...''  Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

% -------------------------------------------------------------------------
% Either list references using the bibliography style file IEEEtran.bst
\bibliographystyle{IEEEtran}
\bibliography{refs17}
%
% or list them by yourself
% \begin{thebibliography}{9}
% 
% \bibitem{waspaa17web}
%   \url{http://www.waspaa.com}.
%
% \bibitem{IEEEPDFSpec}
%   {PDF} specification for {IEEE} {X}plore$^{\textregistered}$,
%   \url{http://www.ieee.org/portal/cms_docs/pubs/confstandards/pdfs/IEEE-PDF-SpecV401.pdf}.
%
% \bibitem{PDFOpenSourceTools}
%   Creating high resolution {PDF} files for book production with 
%   open source tools, 
%   \url{http://www.grassbook.org/neteler/highres_pdf.html}.
%
% \bibitem{eWilliams1999}
% E. Williams, \emph{Fourier Acoustics: Sound Radiation and Nearfield Acoustic
%   Holography}. London, UK: Academic Press, 1999.
% 
% \bibitem{ieeecopyright}
%   \url{http://www.ieee.org/web/publications/rights/copyrightmain.html}.
%
% \bibitem{cJones2003}
% C. Jones, A. Smith, and E. Roberts, ``A sample paper in conference
%   proceedings,'' in \emph{Proc. IEEE ICASSP}, vol. II, 2003, pp. 803--806.
% 
% \bibitem{aSmith2000}
% A. Smith, C. Jones, and E. Roberts, ``A sample paper in journals,'' 
%   \emph{IEEE Trans. Signal Process.}, vol. 62, pp. 291--294, Jan. 2000.
% 
% \end{thebibliography}

\end{sloppy}
\end{document}

### 2017-03-22 paper/paper.tex
Initial commit.

% --------------------------------------------------------------------------
% Template for WASPAA-2017 paper; to be used with:
%          waspaa17.sty  - WASPAA 2017 LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
%
% --------------------------------------------------------------------------

\documentclass{article}
\usepackage{waspaa17,amsmath,graphicx,url,times}
%\usepackage{waspaa17,amssymb,amsmath,graphicx,times,url}
\usepackage{color}
\usepackage[ruled]{algorithm2e}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[labelsep=period]{caption}

% Example definitions.
% --------------------
\def\defeqn{\stackrel{\triangle}{=}}
\newcommand{\symvec}[1]{{\mbox{\boldmath $#1$}}}
\newcommand{\symmat}[1]{{\mbox{\boldmath $#1$}}}
\newcommand\ddfrac[2]{\frac{\displaystyle #1}{\displaystyle #2}}
%\DeclareMathOperator{\argmin}{argmin}
%\DeclareMathOperator{\argmax}{argmax}
\def\argmin{\mathop{\rm arg\,min}}
\def\argmax{\mathop{\rm arg\,min}}
\newcommand\ImNe[1]{\Im \left\{ #1 \right\}}
\newcommand\ReNe[1]{\Re \left\{ #1 \right\}}
\newcommand{\D}{\displaystyle}
\newcommand{\T}{\textstyle}
\newcommand{\TmpCapTitle}[0]{default}
\DeclareCaptionFormat{inc-cap-title}{#1: \textbf{\TmpCapTitle#2}#3\par}
\DeclareCaptionFormat{no-cap-title}{#1\textbf{#2}#3\par}
\newcommand{\CaptionWithTitle}[2]{
    \renewcommand{\TmpCapTitle}[0]{\protect#1}
    \captionsetup{format=inc-cap-title}
    \caption[\protect#1.]{#2}
%    \caption{#2}
}
\captionsetup{format=no-cap-title}
\newcommand{\MyInput}[1]{\immediate\write18{cat #1}}
\def\figwidthscale{0.5}

% Title.
% --------------------
\title{PARTIAL TRACKING VIA LINEAR PROGRAMMING}

%% Single addresses (uncomment and modify for single-address case).
%% --------------------
%\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
%\address{Author Affiliation(s)}
%%
%% For example:
%% ------------
%%\address{School\\
%%       Department\\
%%       Address}

% Two addresses
% --------------------
\twoauthors
  {Nicholas Esterer\sthanks{}}
    {McGill University \\
     Music Technology Area \\
     Schulich School of Music, McGill University \\
     555 Sherbrooke Street West \\
     Montreal, Quebec \\
     Canada H3A 1E3 \\
     nicholas.esterer@mail.mcgill.ca}
  {Philippe Depalle\sthanks{}}
    {McGill University \\
     Music Technology Area \\
     Schulich School of Music, McGill University \\
     555 Sherbrooke Street West \\
     Montreal, Quebec \\
     Canada H3A 1E3 \\
     philippe.depalle@music.mcgill.ca}

\begin{document}

\ninept
\maketitle

\begin{sloppy}

\begin{abstract}
    TODO
\end{abstract}

\begin{keywords}
partial tracking, linear programming, optimization, additive synthesis
\end{keywords}

\section{Partial Tracking\label{chap:partialtracking}}

%In the previous paper, we saw how to estimate parameters of sinusoids with
%polynomial phase. While theoretically applicable to signals of arbitrary length,
%for reasons of flexibility and efficiency, we usually estimate the local
%parameters of the signal under a low-order model and connect multiple
%estimations to form a partial. We will call these local estimations ``analysis
%points'' or ``parameter sets''.

This paper presents an interpretation of the \textit{peak matching} procedure
of McAulay and Quatieri \cite{mcaulay1986speech}, a classical approach to discovering partials. Our
interpretation allows for the specification of an arbitrary cost function
measuring the plausibility that a set of analysis points forms the path of a
partial. With this path interpretation, we were able to design a technique that finds the
optimal set of paths under a constraint on the number of paths. The paper 
concludes with an example of partial tracking on a synthetic signal.

Typically the DTSTFT is computed for a block of contiguous samples, called a
\textit{frame} and these frames are computed every $H$ samples, $H$ being the
\textit{hop-size}. We will denote the $M$ sets of parameters at local maxima in
frame $h$ as $\theta_0^{h}, \dotsc, \theta_{M-1}^{h}$ and the $N$ in frame $h+1$
as $\theta_0^{h+1}, \dotsc, \theta_{N-1}^{h+1}$ where $h$ and $h+1$ refer to
adjacent frames. We are interested in paths that extend across $K$ frames where
each path touches only one parameter set and each parameter set is either
exclusive to a single path or is not on a path.

%In Section~\ref{sec:mqfmfromphase} we discussed how to determine reasonable
%values for the coefficients of a cubic phase polynomial by using the frequency,
%phase and time difference of two local maxima in the DTSTFT. In this section we
%discuss possible ways of determining which local maxima are connected. This is
%referred to as \textit{peak matching} \cite{mcaulay1986speech}
%or \textit{partial tracking} \cite{smith1987parshl} \cite{depalle1993tracking}.

\section{A greedy method}

In this section, we present the McAulay-Quatieri method of peak matching. It is
conceptually simple and a set of short paths can be computed quickly, but
it can be sensitive to spurious peaks and is optimal only in the sense that
the set of paths computed contains the best path possible --- the quality of the
other paths may be compromised under this criterion.

In \cite[p.~748]{mcaulay1986speech} the peak matching algorithm is described in
a number of steps; we summarize them here in a way comparable with the linear
programming formulation to be presented shortly. In that paper, the parameters
of adjacent frames $h$ and $h+1$ are the instantaneous amplitude, phase, and
frequency and are indexed by frequency as $\omega_0^{h}, \dotsc,
\omega_{M-1}^{h}$ and $\omega_0^{h+1}, \dotsc, \omega_{N-1}^{h+1}$ but we will
allow for arbitrary parameter sets.  Define a distance function $\mathcal{D}
\left( \theta_{i},\theta_{j} \right)$ that computes the
similarity between $2$ sets of parameters. We will now consider a method that
finds $L$ tuples of parameters that are closest.

We compute the cost tensor %$\boldsymbol{C}$
$
    \boldsymbol{C} = \theta^{h}
    \otimes_{\mathcal{D}} \mathellipsis \otimes_{\mathcal{D}} \theta^{h+K-1}
$.
For each $l \in \left[0 \dotsc L-1 \right]$, find the indices
$i_{0},\dotsc,i_{K-1}$ 
corresponding to the shortest
distance, then remove the $i_{0},\dotsc,i_{K-1}$th rows (lines of table entries)
in the their respective dimensions from consideration
and continue until $L$ tuples have been determined or the distances exceed some
threshold $\Delta$. This is summarized in Algorithms~\ref{alg:mq_peak_match}

\begin{algorithm}
    \KwIn{the cost matrix $\boldsymbol{C}$}
    \KwOut{$L$ tuples of indices $\Gamma$, or fewer if $\Delta$ exceeded}
    $\Gamma \leftarrow \varnothing$\;
    \For{$l \leftarrow 0$ to $L-1$}{
        $\D \Gamma_{l}=\argmin_{[0,\dotsc,M_{0}-1] \times
        \mathellipsis \times [0,\dotsc,M_{K-1}-1] \setminus \Gamma}
            \boldsymbol{C}$\;
            \If{$ C_{\Gamma_{l}} > \Delta$}{
            \KwRet{$\Gamma$}
        }
        $\Gamma \leftarrow \Gamma \cup C_{\Gamma_{l}}$\;
    }
    \KwRet{$\Gamma$}
    \caption{A generalized McAulay-Quatieri peak-matching algorithm.}%
    \label{alg:mq_peak_match}
\end{algorithm}

This is a greedy algorithm because on every iteration the smallest cost is
identified and its indices are removed from consideration. Perhaps choosing a
slightly higher cost in one iteration would allow smaller costs to be chosen in
successive iterations. This algorithm does not allow for that. In other terms,
the algorithm does not find a set of pairs that represent a globally minimal sum of
costs.
Furthermore, the algorithm does not scale well: assuming equal numbers of
parameter sets in all frames, the search space grows exponentially with
$K$. Nevertheless, the method is simple to implement, computationally negligible
when $K$ is small, and works well with audio signals \cite{mcaulay1986speech}
\cite{smith1987parshl}.

\section{An optimal method \label{sec:lppathsearch}}

There is a way to find a set of paths over multiple frames ($K > 2$) having the
lowest total cost if
we restrict the search to exactly $L$ paths. Instead of indexing parameters by
their frame number $h$, we make $h$ part of the parameter set so that it can be
used by the distance function $\mathcal{D}$. Assume that over $K$ frames there
are $M$ total parameter sets. In this context we will consider them as nodes in
a graph. We define the vector $\boldsymbol{c} \in \mathbb{R}^{M^2}$
where the entry $\boldsymbol{c}_{i + Mj} = \mathcal{D} \left( \theta_{i}, \theta_{j}
\right)$. If we have a set of connections $\Gamma_{i,j}$ we can calculate the
total cost of these connections by defining the vector
\[
    \boldsymbol{x}_{i + Mj} = \begin{cases}
        1 & \text{there is a connection between }i\text{ and }j\\
        0 & \text{otherwise}
    \end{cases}
\]
and then forming the inner product
\[
    c_{\text{total}}=\left\langle \boldsymbol{c},\boldsymbol{x} \right\rangle
\]
Note that a node cannot be connected to itself. The question is how to find
$\boldsymbol{x}^{\ast}$ so that $c_{\text{total}}$ is minimized. How do we
constrain $\boldsymbol{x}$ to give us a solution to the partial tracking
problem? Let us consider an example.

In Figure~\ref{plot:simple_graph} we have an example of a simple graph or
lattice. Such a graph represents a plausible partial tracking situation:
vertically aligned nodes are parameter sets estimated from the same analysis
frame and we would like to connect these parameter sets between frames. The
numbers are indices of nodes in the graph and the edges (possible connections) between
them are indicated by lines. Imagine that we would like to
find the two shortest paths. We will now examine the resulting paths from two
algorithms using different criteria for shortness.

In Figure~\ref{plot:simple_graph_greedy_paths} we find the paths using an
algorithm similar to Algorithms~\ref{alg:mq_peak_match} but search instead over a
tensor of distances $C \in \mathbb{R}^{3 \times 4 \times 2}$ whose entry
$C_{i,j,h}$ represents the cost of travelling on the path connecting the $i$th
node in layer 0, the $j$th node in layer 1 and the $h$th node in layer 2. This
cost is the sum of the Euclidean distances giving the lengths of the
connections. This is the greedy method of searching for the best paths whose
optimality criterion is to find the set of best paths containing the absolute
best path. We see in Figure~\ref{plot:simple_graph_greedy_paths} that the
absolute shortest path, $1 \rightarrow 4 \rightarrow 8$, is discovered, followed
by the second shortest path not using the nodes of the first path, $2
\rightarrow 5 \rightarrow 7$.

\begin{figure}[!t]
    \centering
    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex.eps}}
    \CaptionWithTitle{%
        \input{plots/small_graph_ex.txt}%
    }{\label{plot:simple_graph}}
\end{figure}

\begin{figure}[!t]
    \centering
    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_greedy_paths.eps}}
    \CaptionWithTitle{%
        \input{plots/small_graph_ex_greedy_paths.txt}%
    }{\label{plot:simple_graph_greedy_paths}}
\end{figure}

\subsection{$L$ shortest paths via linear programming}

To find a set of paths minimizing the total cost, we instead search for total
solutions $\boldsymbol{x}$ that describe all paths in the graph. Assume for now
that we can guarantee that the entries of $\boldsymbol{x}$ will be either 0 or
1. To find a set of constraints for our search, we consider the structure of a
valid solution $\boldsymbol{x}^{\ast}$. To maintain that paths not overlap, a
valid solution's nodes are only allowed to have one edge entering ---
coming from a node in a previous frame --- and one edge leaving
--- going to a node in a successive frame. To translate this into a
constraint, consider the node $i$ and its possible $R_{i}$ successive connecting
nodes $j_{0} \dotsc j_{R_{i}-1}$. Define the vector\footnote{The superscript s
stands for ``successive''.}
\[
    a^{\text{s},i}_{i + Mj_{r}} = \begin{cases}
        1 & \forall j_{r} \in \left[ j_{0} \dotsc j_{R_{i}-1} \right] \\
        0 & \text{otherwise}
    \end{cases}
\]
As all the entries of $\boldsymbol{x}$ are either 0 or 1, we have
\[
    0 \leq \left\langle \boldsymbol{a}^{\text{s},i}, \boldsymbol{x} \right\rangle \leq 1
\]
so we can make this a constraint to ensure that a node has at most one path
leaving. Similarly, if we consider the node $j$ and its possible $R_{j}$ previous connecting
nodes $i_{0} \dotsc i_{R_{j}-1}$, the vector\footnote{The superscript p
stands for ``previous''.}
\[
    a^{\text{p},j}_{i_{r} + Mj} \begin{cases}
        1 & \forall i_{r} \in \left[ i_{0} \dotsc i_{R_{j}-1} \right] \\
        0 & \text{otherwise}
    \end{cases}
\]
constrains that node $j$ have only one path entering through the constraint
\[
    0 \leq \left\langle \boldsymbol{a}^{\text{p},j} , \boldsymbol{x} \right\rangle \leq 1
\]
A node on a path will also have an edge entering and an edge leaving. To
translate this into a constraint, we define a vector that counts the number of
edges entering a node and subtracts then the number of edges leaving a node. The
result should always be 0 for an equal number of edges entering and exiting a
node. If $r$ is the index of the node considered, the vector is simply
\footnote{The superscript b stands for ``balanced''.}
\[
    \boldsymbol{a}^{\text{b},r} = \boldsymbol{a}^{\text{p},r} -
    \boldsymbol{a}^{\text{s},r}
\]
and the constraint
\[
    \left\langle \boldsymbol{a}^{\text{b},r}, \boldsymbol{x} \right\rangle = 0
\]
Finally we want to constrain that there be only $L$ paths. We do this by
noticing that if this is true, there will be $L$ edges between frames $h$ and
$h+1$. We constrain the number of paths going from edges
$\Gamma_{h}$ in frame $h$ to $\Gamma_{h+1}$ by forming the vector
\footnote{The superscript c stands for ``connections''.}
\[
    \boldsymbol{a}^{\text{c},h} = \sum_{j \in \Gamma_{h}}
    \boldsymbol{a}^{\text{s},j}
\]
and asserting the constraint
\[
    \left\langle \boldsymbol{a}^{\text{c},h} , \boldsymbol{x} \right\rangle = L
\]
The length of $\boldsymbol{x}$ is $M^{2}$ so the total size of all the
constraints is not insignificant, but most entries in the constraint vectors will
be 0 and therefore the resulting constraint matrices very sparse, so sparse
linear algebra routines can be used in computations. Furthermore, the
$\boldsymbol{a}^{b}$ and $\boldsymbol{a}^{c}$ constraints are derived from
$\boldsymbol{a}^{p}$ and $\boldsymbol{a}^{s}$, so only the latter need to be
stored.

\begin{figure}[!t]
    \centering
    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_lp_paths.eps}}
    \CaptionWithTitle{%
        \input{plots/small_graph_ex_lp_paths.txt}%
    }{\label{plot:simple_graph_lp_paths}}
\end{figure}

The complete \textit{linear program (LP)} solving the $L$ shortest paths problem is then
\[
    \min_{\boldsymbol{x}} \left\langle \boldsymbol{c}, \boldsymbol{x} \right\rangle
\]
subject to
\[
    \boldsymbol{0} \leq
    \begin{bmatrix}
        \boldsymbol{A}_{\text{s}} \\
        \boldsymbol{A}_{\text{p}}
    \end{bmatrix} \boldsymbol{x}
    \leq \boldsymbol{1}
\]
\[
    \begin{bmatrix}
        \boldsymbol{A}_{\text{b}} \\
        \boldsymbol{A}_{\text{c}}
    \end{bmatrix}
    \boldsymbol{x}
    =
    \begin{bmatrix}
        \boldsymbol{0} \\
        L\boldsymbol{1}
    \end{bmatrix}
\]
\[
    \boldsymbol{0} \leq \boldsymbol{x} \leq \boldsymbol{1}
\]
where $\boldsymbol{A}_{\text{s}}$ is the matrix with
$\boldsymbol{a}^{\text{s},m}$ as its rows for $m \in [0 \dotsc M-1]$ and
$\boldsymbol{A}_{\text{p}}$ is the matrix with $\boldsymbol{a}^{\text{p},m}$ as
its rows, etc.

The solution of the two best paths using the LP formulation
is shown in Figure~\ref{plot:simple_graph_lp_paths} and a comparison of the
total costs is shown in Table~\ref{tab:greedy_lp_cost_compare}

\begin{table}[!b]
    \caption{\label{tab:greedy_lp_cost_compare} Comparison of total costs in
    Figure~\ref{plot:simple_graph_lp_paths}}
    \begin{center}
        \begin{tabular}{c c}
            Greedy & LP \\
            \hline
            \input{plots/small_graph_ex_greedy_cost.txt} &
            \input{plots/small_graph_ex_lp_cost.txt} \\
        \end{tabular}
    \end{center}
\end{table}

The LP formulation is inspired by a multiple object tracking algorithm for video
\cite{jiang2007linear}. A proof that the solution $\boldsymbol{x}^{\ast}$ will
have entries equal to either $0$ or $1$ can be found in
\cite[p.~167]{parker1988discrete}. The theoretical computational complexity of
the linear program is polynomial in the number of variables, see
\cite{karmarkar1984new} for a proof and the demonstration of a fast algorithm
for finding its solution. In practice, to extract paths from the solution, we do
not test equality with $0$ or $1$ but rather test if the solution vector's
values are greater than some threshold.

\subsection{Complexity}

The LP formulation of the $L$-best paths problem gives results equivalent to the
solution to the $L$-best paths problem proposed in \cite{wolf1989finding}. The
complexity of our algorithm is different.  Assuming we
use the algorithm in \cite{karmarkar1984new} to solve the LP, our program has a
complexity of $O(M^{7}B^{2})$ where $M$ is the number of nodes (parameter sets)
and $B$ is the number of bits used to represent each number in the input. The
complexity of the algorithm by Wolf in \cite{wolf1989finding} is equivalent to
the Viterbi algorithm for finding the single best path through a trellis whose
$h$th frame has $\binom{N_{h}}{L}\binom{N_{h+1}}{L}L!$ connections where $N_{h}$
and $N_{h+1}$ are the number of nodes in two consecutive frames of the original
lattice. Therefore, assuming a constant number $N$ of nodes in each frame, its
complexity is $O((\binom{N}{L}^{2}L!)^{2}T)$. If there are few nodes in each
frame and a small number of paths are searched, Wolf's formulation is superior
as its complexity increases linearly with the number of frames in the lattice.
On the other hand, if each frame has a large number of nodes or many paths are
searched, the LP formulation is superior.  Informally we have found this to
agree with reality --- both algorithms were tried when producing the figures in
Section~\ref{sec:mq_lp_compare_chirp}.  Indeed the Wolf formulation took
prohibitively long to compute when many paths were desired, as did the LP when
many frames were considered.

In the special case that only 1 shortest path is searched the Viterbi algorithm
\cite{forney1973viterbi} can be used that only requires on the order of $N^{2}T$
calculations \cite{rabiner1989tutorial} where $N$ is the number of nodes in each
frame and $T$ is the number of frames (assuming the same number of nodes in each
frame).

\section{Partial paths on an example signal\label{sec:mq_lp_compare_chirp}}

We compare the greedy and LP based methods for peak matching on a synthetic
signal. The signal is composed of $K=6$ chirps of constant amplitude, the $k$th
chirp $s$ at sample $n$ described by the equation
\[
    s_{k}(n) = \exp(j(\phi_{k} + \omega_{k}n +
    \frac{1}{2} \psi_{k} n^{2}))
\]
The parameters for the 6 chirps are presented in
Table~\ref{tab:ptrackexamplechirpparams}.

\begin{table}[!b]
    \caption{Parameters of $k$th chirp. $f_{0}$ and $f_{1}$ are the initial and
    final frequency of the chirp in Hz. \label{tab:ptrackexamplechirpparams}}
    \begin{center}
        \begin{tabular}{l c c c c c}
            $k$ & $\phi_{k}$ & $\omega_{k}$ & $\psi_{k}$ & $f_{0}$ & $f_{1}$ \\
            \hline
            \input{plots/mq_lp_compare_chirp_params.txt}
        \end{tabular}
    \end{center}
\end{table}

Two 1 second long signals are synthesized at a sampling rate of 16000 Hz, the
first with chirps 0--2, the second with chirps 3--5. We add
Gaussian distributed white noise at several SNRs to evaluate the technique in the
presence of noise.

%\begin{figure}[!t]
%    %\centering
%    \centering
%    \includegraphics[width=\figwidthscale\textwidth]{plots/mq_lp_compare_chirp_20.eps}
%    \CaptionWithTitle{%
%        \input{plots/mq_lp_compare_chirp_20.txt}%
%    }{ Line-segments representing the frequency and frequency-slope at local
%        spectrogram maxima. In the bottom two plots the line segments not deemed
%        by the respective algorithms as belonging to a partial path are
%        discarded, revealing the estimated partial trajectories. See
%        Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
%    \label{plot:mq_lp_compare_chirp_20}}
%\end{figure}
%\begin{figure}[!t]
%    %\centering
%    \centering
%    \includegraphics[width=\figwidthscale\textwidth]{plots/mq_lp_compare_chirp_15.eps}
%    \CaptionWithTitle{%
%        \input{plots/mq_lp_compare_chirp_15.txt}%
%    }{ Line-segments representing the frequency and frequency-slope at local
%        spectrogram maxima. In the bottom two plots the line segments not deemed
%        by the respective algorithms as belonging to a partial path are
%        discarded, revealing the estimated partial trajectories. See
%        Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
%    \label{plot:mq_lp_compare_chirp_15}}
%\end{figure}
\begin{figure}[!t]
    %\centering
    \centering
    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/mq_lp_compare_chirp_10.eps}}
    \CaptionWithTitle{%
        \input{plots/mq_lp_compare_chirp_10.txt}%
    }{ Line-segments representing the frequency and frequency-slope at local
        spectrogram maxima. In the bottom two plots the line segments not deemed
        by the respective algorithms as belonging to a partial path are
        discarded, revealing the estimated partial trajectories. See
        Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
    \label{plot:mq_lp_compare_chirp_10}}
\end{figure}

A spectrogram of each signal is computed with an analysis window length of 1024
samples and a hop-size $H$ of 256 samples. Local maxima are searched in 150 Hz
wide bands spaced 75 Hz apart. A local maximum is only accepted if its amplitude
is greater than -20 dB. The bin corresponding to each local maximum and its two
surrounding bins are used by the Distribution Derivative Method
(DDM) to estimate the
local chirp parameters, the $i$th set of parameters in frame $h$ denoted
$\theta_{i}^{h} = \left\{ \phi_{i}^{h} , \omega_{i}^{h} , \psi_{i}^{h}
\right\}$ (the atoms used by the DDM are generated from 4-term continuous
Nuttall windows). The results of the analyses of both signals are lumped together and
it is on this lumped data that we perform partial tracking.

We search for partial tracks using both the greedy and LP strategies. Both
algorithms use the distance metric $\mathcal{D}_{\text{pr.}}$ between two parameters sets:
\[
    \mathcal{D}_{\text{pr.}} \left( \theta_{i}^{h},
    \theta_{j}^{h+1} \right) = \left( \omega_{i}^{h} +
    \psi_{i}^{h} H - \omega_{j}^{h+1} \right)
\]
which is the error in predicting $j$th frequency in frame $h+1$ from the $i$th
parameters in frame $h$. For the greedy method, the search for partial paths is
restricted to one frame ahead like in \cite{mcaulay1986speech}, otherwise the
computation becomes intractable. For the LP
method, to keep the computation time reasonable, we search over 6 frames for 6
best paths (the number of paths does not affect the computation time).
To maintain connected paths, the search on the next frames uses the end nodes of
the last search as starting points. For both methods, the search is restricted
to nodes between frequencies 250 to 2250 Hz.

Figure~\ref{plot:mq_lp_compare_chirp_20},~\ref{plot:mq_lp_compare_chirp_15},%
~and~\ref{plot:mq_lp_compare_chirp_10}
show discovered partial trajectories for signals with a SNR of 20, 15, and 10
dB,
respectively. It is seen that while the greedy method begins to perform poorly
at a SNR of 15dB, the LP method still gives plausible partial trajectories for
SNRs of 10 and 15 dB. At lower SNRs, the LP formulation gives
some paths that do not correspond to an underlying partial. These could be filtered
out by examining the cost of these paths and comparing them to the costs of the
others. Those that deviate from a mean cost more than a certain amount should be
rejected. This is the strategy used in Chapter~\ref{chap:decaysep} and
illustrated in Figure~\ref{plot:acgtra3xylofs4costlengththresh}. In any case,
the lower SNRs are relatively challenging for any partial tracking technique.

But why did the LP discover a path not present in the underlying signal? This is
due to the cost function, which finds a path with minimum prediction error in
using the frequency and frequency slope coefficients of one node to predict
another node's frequency coefficient. When there are many nodes in the original
analysis it is not surprising that some unexpected path exists.  An attribute of
these erroneous paths is that they are not smooth. To deter the algorithm from
finding such paths, regularization could be used like in
Section~\ref{sec:mqfmfromphase} that minimizes the integral of the squared
estimate of the path's second derivative. More on regularization in optimization
can be found in \cite[ch.~6.3]{boyd2004convex}.

\section{Conclusion}

In this paper we reformulated the classical greedy algorithm of McAulay and
Quatieri and showed that it can be seen as a greedy algorithm for finding the $L$
shortest paths in a lattice. An algorithm was then proposed minimizing the sum
of the $L$ paths, using a linear programming approach. It was shown on synthetic
signals that the new approach finds plausible paths in lattices with a
large number of spurious nodes.

There are problems with the proposed approach. As discussed in
\ref{sec:lppathsearch}, ``jagged'' paths should be removed using regularization.
There are also situations where it is undesirable to have paths extend
throughout the entire lattice. Acoustic signals produced by striking media, such
as strings or bars, exhibit a spectrum where the upper partials decay more
quickly than the lower ones (e.g., see Figure~\ref{plot:acgtra3specgram}) --- it
would be desirable in these situations to have shorter paths for the upper
partials, those decaying more quickly. This could be addressed as in
\cite{depalle1993tracking} where the signal is divided into overlapping sequences of
frames and partial paths are connected between sequences.

The proposed algorithm, while faster than algorithms based on the Viterbi
algorithm, is still not fast. Assuming the same cost function
$\mathcal{D}_{\text{pr.}}$ as in Section~\ref{sec:mq_lp_compare_chirp} it would
be more efficient to consider narrow bands over which to search for paths when
analysing signals with little frequency modulation. However, as we will see in
Chapter~\ref{chap:amfmsep}, with different cost functions, the algorithm is
useful for solving general $L$ shortest paths problems outside of partial
tracking.

\section{ACKNOWLEDGMENT}

% -------------------------------------------------------------------------
% Either list references using the bibliography style file IEEEtran.bst
\bibliographystyle{IEEEtran}
\bibliography{paper}

\end{sloppy}
\end{document}

### 2017-03-22 mq_path_smooth.py

@@ -1,0 +1,316 @@
+import ddm
+import numpy as np
+import matplotlib.pyplot as plt
+import sigmod2 as sm
+import sys
+import ptpath
+from cvxopt import solvers
+import ptpath_test
+import os
+import neplot as nep
+# Color contrast config
+# values further from 1, more contrast
+clr_gamma=4.
+clr_mapper=nep.PowerNormalize(clr_gamma)
+
+show_plot=True
+
+plotoutpath='paper/plots/'
+chirp_param_out_path=plotoutpath+'mq_lp_comp_smooth_chirp_params.txt'
+if len(sys.argv) < 2:
+    D_r=20.
+    plotoutpath+='mq_lp_comp_smooth_chirp_'+str(int(np.round(D_r)))+'_dflt.eps'
+else:
+    D_r=float(sys.argv[1])
+    plotoutpath+='mq_lp_comp_smooth_chirp_'+str(int(np.round(D_r)))+'.eps'
+
+plt.rc('text',usetex=True)
+plt.rc('font',family='serif')
+
+fig, (ax1,ax2,ax3) = plt.subplots(3,1,sharex='col',sharey='row')
+
+# Test McAulay and Quatieri partial path construction
+
+# Synthesize signal
+# Chirp 0
+f0_0=500.
+f0_1=600.
+# Chirp 1
+f1_0=700.
+f1_1=400.
+# Number of harmonics
+K=3
+# Boundaries on frequencies to consider
+f_min=250.
+f_max=2250
+
+## Power of signal (dB)
+#  Each sinusoid has amplitude 1 and there are K sinusoids per sound.
+#  (The noise is added to each sound)
+D_s=20.*np.log(K)
+## Signal to noise ratio (dB)
+D_n=D_s-D_r
+P_n=10.**(D_n/10.)
+
+T=1.
+Fs=16000
+N=int(np.round(T*Fs))
+n=np.arange(N)
+
+# Angular velocity as function of sample number, source 0
+a0_1=f0_0/Fs*np.pi*2.
+a0_2=(f0_1-f0_0)/Fs*np.pi*2./N
+# Initial phase
+a0_0=0.
+# Angular velocity as function of sample number, source 1
+a1_1=f1_0/Fs*np.pi*2.
+a1_2=(f1_1-f1_0)/Fs*np.pi*2./N
+# Initial phase
+a1_0=0.
+# Phase function
[…]

### 2017-03-22 mq_path_smooth_debug.py

@@ -1,0 +1,317 @@
+import ddm
+import numpy as np
+import matplotlib.pyplot as plt
+import sigmod2 as sm
+import sys
+import ptpath
+from cvxopt import solvers
+import ptpath_test
+import os
+import neplot as nep
+# Color contrast config
+# values further from 1, more contrast
+clr_gamma=4.
+clr_mapper=nep.PowerNormalize(clr_gamma)
+
+show_plot=True
+
+plotoutpath='paper/plots/'
+chirp_param_out_path=plotoutpath+'mq_lp_comp_smooth_chirp_params.txt'
+if len(sys.argv) < 2:
+    D_r=20.
+    plotoutpath+='mq_lp_comp_smooth_chirp_'+str(int(np.round(D_r)))+'_dflt.eps'
+else:
+    D_r=float(sys.argv[1])
+    plotoutpath+='mq_lp_comp_smooth_chirp_'+str(int(np.round(D_r)))+'.eps'
+
+plt.rc('text',usetex=True)
+plt.rc('font',family='serif')
+
+fig, (ax1,ax2,ax3) = plt.subplots(3,1,sharex='col',sharey='row')
+
+# Test McAulay and Quatieri partial path construction
+
+# Synthesize signal
+# Chirp 0
+f0_0=500.
+f0_1=600.
+# Chirp 1
+f1_0=700.
+f1_1=400.
+# Number of harmonics
+K=3
+# Boundaries on frequencies to consider
+f_min=250.
+f_max=2250
+
+## Power of signal (dB)
+#  Each sinusoid has amplitude 1 and there are K sinusoids per sound.
+#  (The noise is added to each sound)
+D_s=20.*np.log(K)
+## Signal to noise ratio (dB)
+D_n=D_s-D_r
+P_n=10.**(D_n/10.)
+
+T=1.
+Fs=16000
+N=int(np.round(T*Fs))
+n=np.arange(N)
+
+# Angular velocity as function of sample number, source 0
+a0_1=f0_0/Fs*np.pi*2.
+a0_2=(f0_1-f0_0)/Fs*np.pi*2./N
+# Initial phase
+a0_0=0.
+# Angular velocity as function of sample number, source 1
+a1_1=f1_0/Fs*np.pi*2.
+a1_2=(f1_1-f1_0)/Fs*np.pi*2./N
+# Initial phase
+a1_0=0.
+# Phase function
[…]

### 2017-03-22 paper/build_paper.sh

@@ -1,0 +1,12 @@
+#! /bin/bash
+
+# Builds the paper.tex file complete with bibliography.
+
+# Convert all eps files to pdf
+
+pdflatex paper.tex
+BIBINPUTS=. bibtex paper.aux
+pdflatex paper.tex
+pdflatex paper.tex
+mv paper.pdf Esterer_Nicholas_WASPAA_2017.pdf
+#dvipdf thesis.dvi

### 2017-03-22 sigmod2.py

@@ -1,0 +1,614 @@
+import numpy as np
+import scipy as sp
+import scipy.linalg
+import sys
+import ddm
+
+def lextrem(a,comp='max'):
+    """
+    Output local extrema. Regions of equal values with different values
+    surrounding are not considered extrema! Values on the edges of the array are
+    not considered extrema either.
+    """
+    cmpfunc={'max':np.greater,'min':np.less}[comp]
+    mab=np.r_[False,cmpfunc(a[1:],a[:-1])]&np.r_[cmpfunc(a[:-1],a[1:]),False]
+    mai=np.transpose(np.nonzero(mab))
+    ma=a[mai]
+    return (ma,mai)
+
+def lextrem_win(x,b,o,i,th,ar,M,bi=0):
+    """
+    Search in windows of size b every hop o for values exceeding th and that are
+    whose dB ratio with the average of the minimum values in the frame is
+    greater than ar.
+
+    x:
+        the signal to search for maxima in.
+
+    b:
+        the size of the bands (in samples) in which to search for maxima.
+    o:
+        the hopsize between bands (in samples).
+    th:
+        the minimum amplitude of a true peak (peaks lower than this are not
+        considered).
+    i:
+        If a maximum is found, the band in which maxima are searched is not
+        shifted by o but rather set to begin at the index of the last maximum +
+        some number of ignored bins, given by i (default 1).
+    ar:
+        The threshold ratio 20*log10(max_peak/avg_min_peak). If over this value,
+        the peak is considered, otherwise it is not. If the value is less than 0
+        the peak is always considered (default -1). For example, if ar=40, the
+        max_peak has to be 100 times that of the avg_min_peak.
+    M:
+        the maximum index to consider. Can be used to only consider half the
+        spectrum for example.
+    bi:
+        The initial index to start on (default 0).
+
+
+    Returns:
+
+    ks:
+        Indices of local maxima.
+
+    """
+
+    b_=bi
+    ks=[]
+    if (o == 0):
+        raise Exception('Hopsize cannot be 0.')
[…]

### 2017-03-30 lp_path_test.py
Adding a cleaned up matrix prep routine
Doesn't yet work. I believe it is because the inequality constraints need to be separated or else there are too few
and the program is unbounded. What needs to happen: for example for each node, you cannot count the number of
incoming nodes in total, you must count them using separate constraints. In the end the number of non-zero values
in the constraint matrix is the same, but there are more constraints.

@@ -1,0 +1,116 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import cvxopt
+
+def get_L_best_paths_mats(c,n_pts_per_frame,L):
+    """
+    Get the matrices for the linear program that finds the L best paths through
+    a lattice.
+
+    c:
+        The cost tensor flattened into an array. Let C denote this tensor which
+        must have size MxM. If C[i,j] is the cost between node i and node j,
+        then c[M*i + j] = C[i,j].
+    n_pts_per_frame:
+        A list of the number of nodes in each frame. The numbers correspond to
+        the number of contiguous indices of the axes in C, e.g., if
+        n_pts_per_frame is [2,4,3] then frame 0 contains nodes [0,1], frame 1
+        [2,3,4,5], and frame 2 [6,7,8].
+    L:
+        The number of paths.
+
+    returns tuple (G,h,A,b)
+
+    G:
+        The inequality constraint matrix such that G*x <= h.
+    h:
+        The inequality constraint vector.
+    A:
+        The equality constraint matrix such that A*x = b.
+    b:
+        The equality constraint vector.
+    """
+    # total number of nodes
+    M=sum(n_pts_per_frame)
+    # number of frames
+    F=len(n_pts_per_frame)
+    if not isinstance(c,np.ndarray):
+        raise Exception("c must be type np.ndarray, currently is type %s." %
+                (type(c),))
+    if (F < 3):
+        raise Exception("Must use 3 or more frames, here F=%d.", (F,))
+    if (c.size != (M*M)):
+        raise Exception("Bad size %d for c or total sum %d for n_pts_per_frame." %
+                (c.size,M))
+    if (L > min(n_pts_per_frame)):
+        raise Exception(
+        "Number of points in frame %d less than number of paths L=%d."
+        "No solution possible." % (np.argmin(n_pts_per_frame),L))
+            
+    # point indices in each frame
+    pts_per_frame = [range(l) for l in n_pts_per_frame]
+    # incoming connections
+    # matrix (first frame can't have incoming cxns)
[…]

### 2017-03-30 mq_path_short.py

@@ -1,0 +1,320 @@
+# Compare greed McAulay Quatieri over multiple frames with LP
+import ddm
+import numpy as np
+import matplotlib.pyplot as plt
+import sigmod2 as sm
+import sys
+import ptpath
+from cvxopt import solvers
+import ptpath_test
+import os
+import neplot as nep
+import itertools as it
+# Color contrast config
+# values further from 1, more contrast
+clr_gamma=4.
+clr_mapper=nep.PowerNormalize(clr_gamma)
+
+show_plot=True
+
+plotoutpath='paper/plots/'
+chirp_param_out_path=plotoutpath+'mq_lp_comp_short_chirp_params.txt'
+if len(sys.argv) < 2:
+    D_r=20.
+    plotoutpath+='mq_lp_comp_short_chirp_'+str(int(np.round(D_r)))+'_J=%d_L=%d_dflt.eps'
+else:
+    D_r=float(sys.argv[1])
+    plotoutpath+='mq_lp_comp_short_chirp_'+str(int(np.round(D_r)))+'_J=%d_L=%d_dflt.eps'
+
+plt.rc('text',usetex=True)
+plt.rc('font',family='serif')
+
+fig, (ax1,ax2,ax3) = plt.subplots(3,1,sharex='col',sharey='row')
+
+# Test McAulay and Quatieri partial path construction
+
+# Synthesize signal
+# Chirp 0
+f0_0=500.
+f0_1=600.
+# Chirp 1
+f1_0=700.
+f1_1=400.
+# Number of harmonics
+K=3
+# Boundaries on frequencies to consider
+f_min=250.
+f_max=2250
+
+## Power of signal (dB)
+#  Each sinusoid has amplitude 1 and there are K sinusoids per sound.
+#  (The noise is added to each sound)
+D_s=20.*np.log(K)
+## Signal to noise ratio (dB)
+D_n=D_s-D_r
+P_n=10.**(D_n/10.)
+
+T=1.
+Fs=16000
+N=int(np.round(T*Fs))
+n=np.arange(N)
+
+# Angular velocity as function of sample number, source 0
+a0_1=f0_0/Fs*np.pi*2.
+a0_2=(f0_1-f0_0)/Fs*np.pi*2./N
+# Initial phase
+a0_0=0.
+# Angular velocity as function of sample number, source 1
[…]

### 2017-03-31 lp_path_test.py
Big inequality matrix
Each possible connection gets its own row in the matrix in order to have enough
constraints.

@@ -1,6 +1,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import cvxopt
+from itertools import product
 
 def get_L_best_paths_mats(c,n_pts_per_frame,L):
     """
@@ -30,6 +31,7 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     b:
         The equality constraint vector.
     """
+    n_pts_per_frame=np.array(n_pts_per_frame)
     # total number of nodes
     M=sum(n_pts_per_frame)
     # number of frames
@@ -52,25 +54,41 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     # incoming connections
     # matrix (first frame can't have incoming cxns)
     Ap=np.zeros((sum(n_pts_per_frame[1:]),M*M))
+    Ip=np.zeros((sum(n_pts_per_frame[1:]*n_pts_per_frame[:-1]),M*M))
     r=0
     for i in xrange(len(pts_per_frame)-1):
         fpts=pts_per_frame[i+1]
         for fpt in fpts:
             Ap[r,M*np.array(pts_per_frame[i])+fpt]=1
             r+=1
+    r=0
+    for i in xrange(len(pts_per_frame)-1):
+        fpts_cur=pts_per_frame[i+1]
+        fpts_prv=pts_per_frame[i]
+        for i_,o_ in product(fpts_cur,fpts_prv):
+            Ip[r,M*o_+i_]=1
+            r+=1
     # vector
-    bp=np.ones((np.sum(n_pts_per_frame[1:]),1))
+    bp=np.ones((Ip.shape[0],1))
     # outgoing connections
     # matrix (last frame can't have outgoing cxns)
     As=np.zeros((sum(n_pts_per_frame[:-1]),M*M))
+    Is=np.zeros((sum(n_pts_per_frame[1:]*n_pts_per_frame[:-1]),M*M))
     r=0
     for i in xrange(len(pts_per_frame)-1):
         fpts=pts_per_frame[i]
         for fpt in fpts:
             As[r,M*fpt + np.array(pts_per_frame[i+1])]=1
             r+=1
+    r=0
+    for i in xrange(len(pts_per_frame)-1):
+        fpts_cur=pts_per_frame[i]
+        fpts_nxt=pts_per_frame[i+1]
[…]

### 2017-03-31 lp_path_test.py
Constrain no connections to non-contiguous frames
Doesn't yet work.

@@ -48,7 +48,8 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
         "No solution possible." % (np.argmin(n_pts_per_frame),L))
             
     # point indices in each frame
-    pts_per_frame = [range(l) for l in n_pts_per_frame]
+    pts_per_frame = [range(l,k) for l,k in
+            zip(np.cumsum([0]+n_pts_per_frame)[:-1],np.cumsum(n_pts_per_frame))]
     # incoming connections
     # matrix (first frame can't have incoming cxns)
     Ap=np.zeros((sum(n_pts_per_frame[1:]),M*M))
@@ -87,14 +88,43 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     Ac[-1,:]=np.sum(Ap[-n_pts_per_frame[-1],:],axis=0)
     # vector
     bc=L*np.ones((F,1))
-    
+    # Number of outgoing connections to non-contiguous frames constrained to 0
+    Anoc=np.zeros((sum(n_pts_per_frame[:-2]),M*M))
+    r=0
+    for i in xrange(len(pts_per_frame)-2):
+        fpts=pts_per_frame[i]
+        if (i == (len(pts_per_frame)-3)):
+            rest_pts=pts_per_frame[-1]
+        else:
+            rest_pts=reduce(lambda x,y : x+y, pts_per_frame[i+2:]) # note this performs list concatenation
+        for fpt in fpts:
+            Anoc[r,M*fpt + np.array(rest_pts)]=1
+            r+=1
+    bnoc=np.zeros((Anoc.shape[0],1))
+    # Number of incoming connections to non-contiguous frames constrained to 0
+    Anic=np.zeros((sum(n_pts_per_frame[2:]),M*M))
+    r=0
+    for i in xrange(len(pts_per_frame)-2):
+        fpts=pts_per_frame[i+2]
+        if (i == 0):
+            rest_pts=pts_per_frame[0]
+        else:
+            rest_pts=reduce(lambda x,y : x+y, pts_per_frame[i+2:])
+        for fpt in fpts:
+            Anic[r,M*np.array(rest_pts) + fpt]=1
+            r+=1
+    bnic=np.zeros((Anic.shape[0],1))
+
+    # Also need 0 <= x <= 1
+    I=np.eye(M*M)
[…]

### 2017-03-31 lp_path_test.py
Fixed point index numbering.

@@ -31,7 +31,6 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     b:
         The equality constraint vector.
     """
-    n_pts_per_frame=np.array(n_pts_per_frame)
     # total number of nodes
     M=sum(n_pts_per_frame)
     # number of frames
@@ -50,7 +49,9 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
         "No solution possible." % (np.argmin(n_pts_per_frame),L))
             
     # point indices in each frame
-    pts_per_frame = [range(l) for l in n_pts_per_frame]
+    pts_per_frame = [range(l,k) for l,k in
+            zip(np.cumsum([0]+n_pts_per_frame)[:-1],np.cumsum(n_pts_per_frame))]
+    n_pts_per_frame=np.array(n_pts_per_frame)
     # incoming connections
     # matrix (first frame can't have incoming cxns)
     Ap=np.zeros((sum(n_pts_per_frame[1:]),M*M))

### 2017-04-01 lp_path_test.py
added 0 <= x <= 1 constraint

@@ -107,10 +107,13 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     # vector
     bc=L*np.ones((F,1))
     
+    # Also need 0 <= x <= 1
+    I=np.eye(M*M)
+    v1=np.ones((M*M,1))
     # build inequality contraint matrix
-    G=np.vstack((Is,Ip,-Is,-Ip))
+    G=np.vstack((Is,Ip,-Is,-Ip,I,-I))
     # and its vector
-    h=np.vstack((bs,bp,0*bs,0*bp))
+    h=np.vstack((bs,bp,0*bs,0*bp,v1,0*v1))
     # Build equality contraint matrix
     A=np.vstack((Ab,Ac))
     b=np.vstack((bb,bc))

### 2017-04-01 lp_path_test.py
Added no connection for non-contiguous frames constraints.

@@ -106,6 +106,34 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     Ac[-1,:]=np.sum(Ap[-n_pts_per_frame[-1],:],axis=0)
     # vector
     bc=L*np.ones((F,1))
+    # Number of outgoing connections to non-contiguous frames constrained to 0
+    Anoc=np.zeros((sum(n_pts_per_frame[:-2]),M*M))
+    r=0
+    for i in xrange(len(pts_per_frame)-2):
+        fpts=pts_per_frame[i]
+        if (i == (len(pts_per_frame)-3)):
+            rest_pts=pts_per_frame[-1]
+        else:
+            rest_pts=reduce(lambda x,y : x+y, pts_per_frame[i+2:]) # note this performs list concatenation
+        for fpt in fpts:
+            Anoc[r,M*fpt + np.array(rest_pts)]=1
+            r+=1
+    bnoc=np.zeros((Anoc.shape[0],1))
+    # Number of incoming connections to non-contiguous frames constrained to 0
+    Anic=np.zeros((sum(n_pts_per_frame[2:]),M*M))
+    r=0
+    for i in xrange(len(pts_per_frame)-2):
+        fpts=pts_per_frame[i+2]
+        if (i == 0):
+            rest_pts=pts_per_frame[0]
+        else:
+            rest_pts=reduce(lambda x,y : x+y, pts_per_frame[i+2:])
+        for fpt in fpts:
+            Anic[r,M*np.array(rest_pts) + fpt]=1
+            r+=1
+    bnic=np.zeros((Anic.shape[0],1))
+    A=np.vstack((Ab,Ac,Anoc,Anic))
+    b=np.vstack((bb,bc,bnoc,bnic))
     
     # Also need 0 <= x <= 1
     I=np.eye(M*M)
@@ -115,8 +143,8 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     # and its vector
     h=np.vstack((bs,bp,0*bs,0*bp,v1,0*v1))
     # Build equality contraint matrix
-    A=np.vstack((Ab,Ac))
-    b=np.vstack((bb,bc))
+    A=np.vstack((Ab,Ac,Anoc,Anic))
+    b=np.vstack((bb,bc,bnoc,bnic))
     return (G,h,A,b)
 
[…]

### 2017-04-01 lp_path_test.py
Tried with GLPK, doesn't work.

@@ -143,4 +143,4 @@ h=cvxopt.matrix(h)
 A=cvxopt.matrix(A)
 b=cvxopt.matrix(b)
 c=cvxopt.matrix(c)
-sol=cvxopt.solvers.lp(c,G,h,A=A,b=b)
+sol=cvxopt.solvers.lp(c,G,h,A=A,b=b,solver='glpk')

### 2017-04-01 lp_path_test.py
Fixed L best paths solver
But it only seems to work with the simplex algorithm, which is okay for now,
but if we want to use some cone constraints later...

@@ -2,6 +2,16 @@ import numpy as np
 import matplotlib.pyplot as plt
 import cvxopt
 
+def print_0_1_array(x):
+    """
+    Prints an array containing only 0s and 1s in a consise way.
+    """
+    for row in x:
+        s=""
+        for col in row:
+            s += "%2.0f" % (col,)
+        print s
+
 def get_L_best_paths_mats(c,n_pts_per_frame,L):
     """
     Get the matrices for the linear program that finds the L best paths through
@@ -58,6 +68,7 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
         fpts=pts_per_frame[i+1]
         for fpt in fpts:
             Ap[r,M*np.array(pts_per_frame[i])+fpt]=1
+#            Ap[r,M*np.array(range(M))+fpt]=1
             r+=1
     # vector
     bp=np.ones((np.sum(n_pts_per_frame[1:]),1))
@@ -69,6 +80,28 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
         fpts=pts_per_frame[i]
         for fpt in fpts:
             As[r,M*fpt + np.array(pts_per_frame[i+1])]=1
+#            As[r,M*fpt + np.array(range(M))]=1
+            r+=1
+    # matrix (first frame can't have incoming cxns)
+    Ap_=np.zeros((sum(n_pts_per_frame[1:]),M*M))
+    r=0
+    for i in xrange(len(pts_per_frame)-1):
+        fpts=pts_per_frame[i+1]
+        for fpt in fpts:
+#            Ap_[r,M*np.array(pts_per_frame[i])+fpt]=1
+            Ap_[r,M*np.array(range(M))+fpt]=1
+            r+=1
+    # vector
+    bp=np.ones((np.sum(n_pts_per_frame[1:]),1))
+    # outgoing connections
+    # matrix (last frame can't have outgoing cxns)
+    As_=np.zeros((sum(n_pts_per_frame[:-1]),M*M))
+    r=0
+    for i in xrange(len(pts_per_frame)-1):
+        fpts=pts_per_frame[i]
+        for fpt in fpts:
[…]

### 2017-04-01 lp_path_test.py
The L best paths algorithm works
For some reason, the cvxopt internal solver doesn't work when only adjacent frames
are considered in determining if the number of nodes in and out is balanced. In this
case one must balance the number of incoming and outgoing nodes considering all
possible connections, so the constrain matrix is a bit less sparse.

If the glpk solver is used, only adjacent frames need be considered. It seems from
casual observation that this solver is slightly slower. Also, we are interested in
adding conical constraints for which this solver won't work.

@@ -89,7 +89,8 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
         fpts=pts_per_frame[i+1]
         for fpt in fpts:
 #            Ap_[r,M*np.array(pts_per_frame[i])+fpt]=1
-            Ap_[r,M*np.array(range(M))+fpt]=1
+            _ins=np.array(list(set(range(M))-set([fpt])))
+            Ap_[r,M*_ins+fpt]=1
             r+=1
     # vector
     bp=np.ones((np.sum(n_pts_per_frame[1:]),1))
@@ -101,20 +102,25 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
         fpts=pts_per_frame[i]
         for fpt in fpts:
 #            As_[r,M*fpt + np.array(pts_per_frame[i+1])]=1
-            As_[r,M*fpt + np.array(range(M))]=1
+            _ins=np.array(list(set(range(M))-set([fpt])))
+            As_[r,M*fpt + _ins]=1
             r+=1
     # vector
     bs=np.ones((np.sum(n_pts_per_frame[:-1]),1))
     # equal number of incoming and outgoing connections for inner frames
     # matrix
     Ab=Ap[:-n_pts_per_frame[-1],:]-As[n_pts_per_frame[0]:,:]
+    Ab_=Ap_[:-n_pts_per_frame[-1],:]-As_[n_pts_per_frame[0]:,:]
     # vector
     bb=np.zeros((sum(n_pts_per_frame[1:-1]),1))
     # constrain number of non-zero values in each frame to be L (for L paths)
     # matrix
     Ac=np.zeros((F-1,M*M))
+    Ac_=np.zeros((F-1,M*M))
     # count by aribtrarily couning the number of outgoing connections, except
     # for the last frame
+    for f,fpts in enumerate(pts_per_frame[:-1]):
+        Ac_[f,:]=np.sum(As_[fpts,:],axis=0) # sum along rows
     for f,fpts in enumerate(pts_per_frame[:-1]):
         Ac[f,:]=np.sum(As[fpts,:],axis=0) # sum along rows
     # in last frame there are only incoming connections so use these to count
[…]

### 2017-04-02 lp_path_test_extract_path.py
QP formulation gives singular KKT
don't know how to fix...

@@ -1,0 +1,217 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import cvxopt
+
+def print_0_1_array(x):
+    """
+    Prints an array containing only 0s and 1s in a consise way.
+    """
+    for row in x:
+        s=""
+        for col in row:
+            s += "%2.0f" % (col,)
+        print s
+
+def get_L_best_paths_mats(c,n_pts_per_frame,L):
+    """
+    Get the matrices for the quadratic program that finds the L best paths through
+    a lattice and also returns each individual path.
+
+    c:
+        The cost tensor flattened into an array. Let C denote this tensor which
+        must have size MxM. If C[i,j] is the cost between node i and node j,
+        then c[M*i + j] = C[i,j].
+    n_pts_per_frame:
+        A list of the number of nodes in each frame. The numbers correspond to
+        the number of contiguous indices of the axes in C, e.g., if
+        n_pts_per_frame is [2,4,3] then frame 0 contains nodes [0,1], frame 1
+        [2,3,4,5], and frame 2 [6,7,8].
+    L:
+        The number of paths.
+
+    returns tuple (P,q,G,h,A,b)
+
+    P:
+        The matrix in the objective function of a quadratic program.
+    q:  
+        The vector in the objective function of a quadratic program.
+    G:
+        The inequality constraint matrix such that G*x <= h.
+    h:
+        The inequality constraint vector.
+    A:
+        The equality constraint matrix such that A*x = b.
+    b:
+        The equality constraint vector.
+    """
+    # total number of nodes
+    M=sum(n_pts_per_frame)
+    # number of frames
+    F=len(n_pts_per_frame)
+    if not isinstance(c,np.ndarray):
+        raise Exception("c must be type np.ndarray, currently is type %s." %
+                (type(c),))
+    if (F < 3):
+        raise Exception("Must use 3 or more frames, here F=%d.", (F,))
+    if (c.size != (M*M)):
[…]

### 2017-04-17 paper/paper.tex
Adding a cleaned up matrix prep routine
Doesn't yet work. I believe it is because the inequality constraints need to be separated or else there are too few
and the program is unbounded. What needs to happen: for example for each node, you cannot count the number of
incoming nodes in total, you must count them using separate constraints. In the end the number of non-zero values
in the constraint matrix is the same, but there are more constraints.
Removed redundant equations and unnecessary variables
Have finished describing the algorithm in the paper. Need to finish writing
complexity analysis.

@@
 \usepackage[labelsep=period]{caption}
+%\usepackage{mathabx}
 
@@
 \def\figwidthscale{0.5}
+
+% symbol definitions
+\newcommand{\cLP}{\boldsymbol{c}_{\rho}}
+\newcommand{\BS}[1]{\boldsymbol{#1}}
 
@@
 \textit{frame} and these frames are computed every $H$ samples, $H$ being the
-\textit{hop-size}. We will denote the $M$ sets of parameters at local maxima in
-frame $h$ as $\theta_0^{h}, \dotsc, \theta_{M-1}^{h}$ and the $N$ in frame $h+1$
-as $\theta_0^{h+1}, \dotsc, \theta_{N-1}^{h+1}$ where $h$ and $h+1$ refer to
+\textit{hop-size}. We will denote the $N_{k}$ sets of parameters at local maxima in
+frame $k$ as $\theta_0^{k}, \dotsc, \theta_{N_{k}-1}^{k}$ and the $N_{k+1}$ in frame $k+1$
+as $\theta_0^{k+1}, \dotsc, \theta_{N_{k+1}-1}^{k+1}$ where $k$ and $k+1$ refer to
 adjacent frames. We are interested in paths that extend across $K$ frames where
@@
 exclusive to a single path or is not on a path.
+
+\subsection{Note on notation}
+
+In this paper, indexing starts at 0. If we have a vector $\BS{x}$ then
+$\BS{x}_{i}$ is the $i$th row or column of that vector depending on the
+orientation. The same notation is used for cartesian products, e.g., if $\alpha$
+and $\beta$ are sets and $A =
+\alpha \times \beta$ then for the pair $a \in A$ $a_{0}$ is the first item in
+the pair and $a_{1}$ the second.
+
+The number of frames is denoted $K$, the number of nodes in the $k$th frame $N_k$ and
+the total number of nodes $M = \sum_{k=0}^{K-1} N_{k}$. $\theta_{i}^{j}$ is the
+$i$th node of the $j$th frame, $\theta^{j}$ the set of all the nodes in the
+$j$th frame and $\theta_{m}$ the $m$th node out of all $M$ nodes ($0 \leq m <
+M$).
 
@@
 
-In \cite[p.~748]{mcaulay1986speech} the peak matching algorithm is described in
+In \cite[q.~748]{mcaulay1986speech} the peak matching algorithm is described in
 a number of steps; we summarize them here in a way comparable with the linear
 programming formulation to be presented shortly. In that paper, the parameters
-of adjacent frames $h$ and $h+1$ are the instantaneous amplitude, phase, and
-frequency and are indexed by frequency as $\omega_0^{h}, \dotsc,
-\omega_{M-1}^{h}$ and $\omega_0^{h+1}, \dotsc, \omega_{N-1}^{h+1}$ but we will
-allow for arbitrary parameter sets.  Define a distance function $\mathcal{D}
+of each data point are the instantaneous amplitude, phase, and frequency but we
+will allow for arbitrary parameter sets $\theta$.  Define a distance function
+$\mathcal{D}
 \left( \theta_{i},\theta_{j} \right)$ that computes the
@@
 
-We compute the cost tensor %$\boldsymbol{C}$
+We compute the cost tensor
 $
-    \boldsymbol{C} = \theta^{h}
-    \otimes_{\mathcal{D}} \mathellipsis \otimes_{\mathcal{D}} \theta^{h+K-1}
+    \BS{C} = \theta^{k}
+    \otimes_{\mathcal{D}} \mathellipsis \otimes_{\mathcal{D}} \theta^{k+K-1}
 $.
@@
 and continue until $L$ tuples have been determined or the distances exceed some
-threshold $\Delta$. This is summarized in Algorithms~\ref{alg:mq_peak_match}
+threshold $\Delta_{\text{MQ}}$. This is summarized in Algorithms~\ref{alg:mq_peak_match}
 
 \begin{algorithm}
-    \KwIn{the cost matrix $\boldsymbol{C}$}
-    \KwOut{$L$ tuples of indices $\Gamma$, or fewer if $\Delta$ exceeded}
+    \KwIn{the cost matrix $\BS{C}$}
+    \KwOut{$L$ tuples of indices $\Gamma$, or fewer if $\Delta_{\text{MQ}}$ exceeded}
     $\Gamma \leftarrow \varnothing$\;
@@
         \mathellipsis \times [0,\dotsc,M_{K-1}-1] \setminus \Gamma}
-            \boldsymbol{C}$\;
-            \If{$ C_{\Gamma_{l}} > \Delta$}{
+            \BS{C}$\;
+            \If{$ C_{\Gamma_{l}} > \Delta_{\text{MQ}}$}{
             \KwRet{$\Gamma$}
@@
 
-\section{An optimal method \label{sec:lppathsearch}}
+\section{$L$ best paths through a lattice via linear programming (LP)}
 
-There is a way to find a set of paths over multiple frames ($K > 2$) having the
-lowest total cost if
-we restrict the search to exactly $L$ paths. Instead of indexing parameters by
-their frame number $h$, we make $h$ part of the parameter set so that it can be
-used by the distance function $\mathcal{D}$. Assume that over $K$ frames there
-are $M$ total parameter sets. In this context we will consider them as nodes in
-a graph. We define the vector $\boldsymbol{c} \in \mathbb{R}^{M^2}$
-where the entry $\boldsymbol{c}_{i + Mj} = \mathcal{D} \left( \theta_{i}, \theta_{j}
-\right)$. If we have a set of connections $\Gamma_{i,j}$ we can calculate the
-total cost of these connections by defining the vector
+In this section we show how to find L paths through a lattice of $K$ frames such
+that the sets of nodes on each path are disjoint. The $k$th frame of the lattice
+contains $N_{k}$ nodes for a total of $M = \sum_{k=0}^{K-1}N_{k}$ nodes.
+
+Whereas the limiting cost underwhich a path would be considered was the sum of
+the costs of all connections in the McAulay-Quatieri method, for the LP method
+we define the cost $\Delta_{\text{LP}}$ as the limiting cost underwhich the
+connection between two nodes will be considered.
+
+The solution vector $\BS{x}$ to the linear program shall indicate the presence of a
+connection between a pair of nodes by having an entry equal to $1$ and otherwise
+have entries equal to $0$. To enumerate the set of possible connection-pairs we
+define
+\begin{equation}
+    \rho = \left\{ (i,j) : \mathcal{D}(\theta_{i},\theta_{j}) \leq
+    \Delta_{\text{LP}} , 0 \leq i < M, 0 \leq j < M, i \neq j \right\}
+\end{equation}
+The cost vector of the objective function is then 
+\begin{equation}
+    \cLP = \left\{ D(\theta_{i},\theta_{j}) \forall (i,j) \in
+    \rho \right\}
+\end{equation}
+and the length of $\cLP$ is $\# \rho = \# \cLP = P$, in other words, $P$
+pairs of nodes. For convenience we define a bijective mapping ${\mathcal{B} :
+\rho \rightarrow [0, \mathellipsis, M-1]}$ giving the index in $\BS{x}$ of the
+pair $p \in \rho$. For the implementation considered in this paper,
+$\mathcal{D}(\theta_{i},\theta_{j}) = \infty$ for all $i,j$ not in adjacent
+frames and so $P$ will be no larger than $(K-1)N^{2}$ (assuming the same
+number of nodes $N$ in each frame).
+
+The total cost of the paths in the solution is then calculated through the
+inner product $\cLP^{T}\BS{x}$. To obtain $\BS{x}^{\ast}$ that represents $L$
+disjoint paths we must place constraints on the structure of the solution. Some
+of the constraints presented in the following are redundant but the redundancies
+are kept for clarity; later we will show which constraints can be removed
+without changing the optimal solution $\BS{x}^{\ast}$.
+
+All nodes in $\BS{x}^{\ast}$ will have at most one incoming connection or
+otherwise no connections, a constraint that can be enforced through the
+following linear inequality. Define $\BS{A}^{\text{I}} \in
+\mathbb{R}^{R_{\text{I}} \times P}$ with $R_{\text{I}} = \sum_{k=1}^{K-1}
+N_{k}$, the number of nodes in all the frames excluding the first. We sum all
+the connections into the node $r_{\text{I}} + N_{0}$ represented by the
+respective entry in $\BS{x}$ through an inner product with the $r_{\text{I}}$th
+row in $\BS{A}^{\text{I}}$ and require that this sum be between $0$ and $1$,
+i.e.,
+\begin{equation}
+    \BS{A}^{\text{I}}_{r_{\text{I}},\mathcal{B}(p)} = \begin{cases}
+        1 & \text{if } p_{1} = r_{\text{I}}+N_{0} \\
+        0 & \text{otherwise}
+    \end{cases}, 0 \leq r_{\text{I}} < R_{\text{I}}, p \in \rho
+\end{equation}
+and
+\begin{equation}
+    \BS{0} \leq \BS{A}^{\text{I}}\BS{x} \leq \BS{1}
+\end{equation}
+Similarly, to constrain the number of outgoing connections into each node, we
+define $R_{\text{O}} = \sum_{k=0}^{K-2} N_{k}$ and
+$\BS{A}^{\text{O}} \in \mathbb{R}^{R_{\text{O}} \times P}$ with
+\begin{equation}
+    \BS{A}^{\text{O}}_{r_{\text{O}},\mathcal{B}(p)} = \begin{cases}
+        1 & \text{if } p_{0} = r_{\text{O}} \\
+        0 & \text{otherwise}
+    \end{cases}, 0 \leq r_{\text{O}} < R_{\text{O}}, p \in \rho
+\end{equation}
+and
+\begin{equation}
+    \BS{0} \leq \BS{A}^{\text{O}}\BS{x} \leq \BS{1}
+\end{equation}
+
+To ensure no breaks in the paths it is required that the number of incoming
+connections into a given node equal the number of outgoing connections for the
+$R_{\text{B}} = \sum_{k=1}^{K-2} N_{k}$ nodes potentially having both incoming
+and outgoing connections.
+\begin{equation}
+    \BS{A}^{\text{B}}_{r_{\text{B}}} = \BS{A}^{\text{B}}_{r_{\text{B}}} -
+    \BS{A}^{\text{B}}_{r_{\text{B}}+N_{0}} \text{ for rows } 0 \leq r_{\text{B}}
+    < R_{\text{B}}
+\end{equation}
+and
+\begin{equation}
+    \label{eq:cxnbalcon}
+    \BS{A}^{\text{B}}\BS{x} = \BS{0}
+\end{equation}
+
+Finally we ensure that there are $L$ paths by counting the number of connections
+in each frame and constraining this sum to be $L$. We choose arbitrarily to
+count the number of outgoing connections by summing rows of $\BS{A}^{\text{O}}$
+into rows of $\BS{A}^{\text{C}} \in \mathbb{R}^{(K-1) \times P}$
+\begin{equation}
+    \BS{A}^{\text{C}}_{r_{\text{C}}} = \sum_{k=a}^{b} \BS{A}^{\text{O}}_{k}
+\end{equation}
+with $a = \sum_{j=0}^{r_{\text{C}}} N_{j}$ and $b = \sum_{j=0}^{r_{\text{C}}+1}
+N_{j}$ and
+\begin{equation}
+    \label{eq:cxnlcon}
+    \BS{A}^{\text{C}}\BS{x} = L\BS{1}
+\end{equation}
+
+As stated above, some of these constraints are redundant and can be removed.
+Indeed, we have $\BS{0} \leq \BS{x} \leq \BS{1}$, therefore we will always have
+$\BS{A}^{\text{I}}\BS{x} \geq 0$ and $\BS{A}^{\text{I}}\BS{x} \geq 0$.
+Furthermore, all but the last row of (\ref{eq:cxnlcon}) can be seen as
+constructed from linear combinations of rows of (\ref{eq:cxnbalcon}) and the last
+row of (\ref{eq:cxnlcon}) so we only require $\BS{A}^{\text{C}}_{K-2}\BS{x} = L$.
+Finally we always have $\BS{x} \leq \BS{1}$ because of the constraint that there
+be a maximum of $1$ incoming and outgoing connection from each node.
+
+The complete LP to find the $L$ best disjoint paths through a lattice described
+by node connections $\rho$ is
 \[
-    \boldsymbol{x}_{i + Mj} = \begin{cases}
-        1 & \text{there is a connection between }i\text{ and }j\\
-        0 & \text{otherwise}
-    \end{cases}
-\]
-and then forming the inner product
-\[
-    c_{\text{total}}=\left\langle \boldsymbol{c},\boldsymbol{x} \right\rangle
-\]
-Note that a node cannot be connected to itself. The question is how to find
-$\boldsymbol{x}^{\ast}$ so that $c_{\text{total}}$ is minimized. How do we
-constrain $\boldsymbol{x}$ to give us a solution to the partial tracking
-problem? Let us consider an example.
-
-In Figure~\ref{plot:simple_graph} we have an example of a simple graph or
-lattice. Such a graph represents a plausible partial tracking situation:
-vertically aligned nodes are parameter sets estimated from the same analysis
-frame and we would like to connect these parameter sets between frames. The
-numbers are indices of nodes in the graph and the edges (possible connections) between
-them are indicated by lines. Imagine that we would like to
-find the two shortest paths. We will now examine the resulting paths from two
-algorithms using different criteria for shortness.
-
-In Figure~\ref{plot:simple_graph_greedy_paths} we find the paths using an
-algorithm similar to Algorithms~\ref{alg:mq_peak_match} but search instead over a
-tensor of distances $C \in \mathbb{R}^{3 \times 4 \times 2}$ whose entry
-$C_{i,j,h}$ represents the cost of travelling on the path connecting the $i$th
-node in layer 0, the $j$th node in layer 1 and the $h$th node in layer 2. This
-cost is the sum of the Euclidean distances giving the lengths of the
-connections. This is the greedy method of searching for the best paths whose
-optimality criterion is to find the set of best paths containing the absolute
-best path. We see in Figure~\ref{plot:simple_graph_greedy_paths} that the
-absolute shortest path, $1 \rightarrow 4 \rightarrow 8$, is discovered, followed
-by the second shortest path not using the nodes of the first path, $2
-\rightarrow 5 \rightarrow 7$.
-
-\begin{figure}[!t]
-    \centering
-    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex.eps}}
-    \CaptionWithTitle{%
-        \input{plots/small_graph_ex.txt}%
-    }{\label{plot:simple_graph}}
-\end{figure}
-
-\begin{figure}[!t]
-    \centering
-    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_greedy_paths.eps}}
-    \CaptionWithTitle{%
-        \input{plots/small_graph_ex_greedy_paths.txt}%
-    }{\label{plot:simple_graph_greedy_paths}}
-\end{figure}
-
-\subsection{$L$ shortest paths via linear programming}
-
-To find a set of paths minimizing the total cost, we instead search for total
-solutions $\boldsymbol{x}$ that describe all paths in the graph. Assume for now
-that we can guarantee that the entries of $\boldsymbol{x}$ will be either 0 or
-1. To find a set of constraints for our search, we consider the structure of a
-valid solution $\boldsymbol{x}^{\ast}$. To maintain that paths not overlap, a
-valid solution's nodes are only allowed to have one edge entering ---
-coming from a node in a previous frame --- and one edge leaving
---- going to a node in a successive frame. To translate this into a
-constraint, consider the node $i$ and its possible $R_{i}$ successive connecting
-nodes $j_{0} \dotsc j_{R_{i}-1}$. Define the vector\footnote{The superscript s
-stands for ``successive''.}
-\[
-    a^{\text{s},i}_{i + Mj_{r}} = \begin{cases}
-        1 & \forall j_{r} \in \left[ j_{0} \dotsc j_{R_{i}-1} \right] \\
-        0 & \text{otherwise}
-    \end{cases}
-\]
-As all the entries of $\boldsymbol{x}$ are either 0 or 1, we have
-\[
-    0 \leq \left\langle \boldsymbol{a}^{\text{s},i}, \boldsymbol{x} \right\rangle \leq 1
-\]
-so we can make this a constraint to ensure that a node has at most one path
-leaving. Similarly, if we consider the node $j$ and its possible $R_{j}$ previous connecting
-nodes $i_{0} \dotsc i_{R_{j}-1}$, the vector\footnote{The superscript p
-stands for ``previous''.}
-\[
-    a^{\text{p},j}_{i_{r} + Mj} \begin{cases}
-        1 & \forall i_{r} \in \left[ i_{0} \dotsc i_{R_{j}-1} \right] \\
-        0 & \text{otherwise}
-    \end{cases}
-\]
-constrains that node $j$ have only one path entering through the constraint
-\[
-    0 \leq \left\langle \boldsymbol{a}^{\text{p},j} , \boldsymbol{x} \right\rangle \leq 1
-\]
-A node on a path will also have an edge entering and an edge leaving. To
-translate this into a constraint, we define a vector that counts the number of
-edges entering a node and subtracts then the number of edges leaving a node. The
-result should always be 0 for an equal number of edges entering and exiting a
-node. If $r$ is the index of the node considered, the vector is simply
-\footnote{The superscript b stands for ``balanced''.}
-\[
-    \boldsymbol{a}^{\text{b},r} = \boldsymbol{a}^{\text{p},r} -
-    \boldsymbol{a}^{\text{s},r}
-\]
-and the constraint
-\[
-    \left\langle \boldsymbol{a}^{\text{b},r}, \boldsymbol{x} \right\rangle = 0
-\]
-Finally we want to constrain that there be only $L$ paths. We do this by
-noticing that if this is true, there will be $L$ edges between frames $h$ and
-$h+1$. We constrain the number of paths going from edges
-$\Gamma_{h}$ in frame $h$ to $\Gamma_{h+1}$ by forming the vector
-\footnote{The superscript c stands for ``connections''.}
-\[
-    \boldsymbol{a}^{\text{c},h} = \sum_{j \in \Gamma_{h}}
-    \boldsymbol{a}^{\text{s},j}
-\]
-and asserting the constraint
-\[
-    \left\langle \boldsymbol{a}^{\text{c},h} , \boldsymbol{x} \right\rangle = L
-\]
-The length of $\boldsymbol{x}$ is $M^{2}$ so the total size of all the
-constraints is not insignificant, but most entries in the constraint vectors will
-be 0 and therefore the resulting constraint matrices very sparse, so sparse
-linear algebra routines can be used in computations. Furthermore, the
-$\boldsymbol{a}^{b}$ and $\boldsymbol{a}^{c}$ constraints are derived from
-$\boldsymbol{a}^{p}$ and $\boldsymbol{a}^{s}$, so only the latter need to be
-stored.
-
-\begin{figure}[!t]
-    \centering
-    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_lp_paths.eps}}
-    \CaptionWithTitle{%
-        \input{plots/small_graph_ex_lp_paths.txt}%
-    }{\label{plot:simple_graph_lp_paths}}
-\end{figure}
-
-The complete \textit{linear program (LP)} solving the $L$ shortest paths problem is then
-\[
-    \min_{\boldsymbol{x}} \left\langle \boldsymbol{c}, \boldsymbol{x} \right\rangle
+    \min_{\BS{x}} \cLP^{T} \BS{x} 
 \]
@@
 \[
-    \boldsymbol{0} \leq
+    \BS{G}\BS{x} =
     \begin{bmatrix}
-        \boldsymbol{A}_{\text{s}} \\
-        \boldsymbol{A}_{\text{p}}
-    \end{bmatrix} \boldsymbol{x}
-    \leq \boldsymbol{1}
-\]
-\[
+        \BS{A}^{\text{I}} \\
+        \BS{A}^{\text{O}} \\
+        -\BS{I}
+    \end{bmatrix} \BS{x} \leq
     \begin{bmatrix}
-        \boldsymbol{A}_{\text{b}} \\
-        \boldsymbol{A}_{\text{c}}
-    \end{bmatrix}
-    \boldsymbol{x}
-    =
-    \begin{bmatrix}
-        \boldsymbol{0} \\
-        L\boldsymbol{1}
+        \BS{1} \\
+        \BS{1} \\
+        \BS{0}
     \end{bmatrix}
 \]
-\[
-    \boldsymbol{0} \leq \boldsymbol{x} \leq \boldsymbol{1}
-\]
-where $\boldsymbol{A}_{\text{s}}$ is the matrix with
-$\boldsymbol{a}^{\text{s},m}$ as its rows for $m \in [0 \dotsc M-1]$ and
-$\boldsymbol{A}_{\text{p}}$ is the matrix with $\boldsymbol{a}^{\text{p},m}$ as
-its rows, etc.
+\begin{equation}
+    \BS{A}\BS{x} =
+    \begin{bmatrix}
+        \BS{A}^{\text{B}} \\
+        \BS{A}^{\text{C}}_{K-2}
+    \end{bmatrix} \BS{x} = 
+    \begin{bmatrix}
+        \BS{0} \\
+        L
+    \end{bmatrix}
+\end{equation}
 
-The solution of the two best paths using the LP formulation
-is shown in Figure~\ref{plot:simple_graph_lp_paths} and a comparison of the
-total costs is shown in Table~\ref{tab:greedy_lp_cost_compare}
+% TODO: move to complexity
 
-\begin{table}[!b]
-    \caption{\label{tab:greedy_lp_cost_compare} Comparison of total costs in
-    Figure~\ref{plot:simple_graph_lp_paths}}
-    \begin{center}
-        \begin{tabular}{c c}
-            Greedy & LP \\
-            \hline
-            \input{plots/small_graph_ex_greedy_cost.txt} &
-            \input{plots/small_graph_ex_lp_cost.txt} \\
-        \end{tabular}
-    \end{center}
-\end{table}
-
-The LP formulation is inspired by a multiple object tracking algorithm for video
-\cite{jiang2007linear}. A proof that the solution $\boldsymbol{x}^{\ast}$ will
-have entries equal to either $0$ or $1$ can be found in
-\cite[p.~167]{parker1988discrete}. The theoretical computational complexity of
-the linear program is polynomial in the number of variables, see
-\cite{karmarkar1984new} for a proof and the demonstration of a fast algorithm
-for finding its solution. In practice, to extract paths from the solution, we do
-not test equality with $0$ or $1$ but rather test if the solution vector's
-values are greater than some threshold.
-
+%\section{An optimal method \label{sec:lppathsearch}}
+%
+%There is a way to find a set of paths over multiple frames ($K > 2$) having the
+%lowest total cost if
+%we restrict the search to exactly $L$ paths. Instead of indexing parameters by
+%their frame number $k$, we make $k$ part of the parameter set so that it can be
+%used by the distance function $\mathcal{D}$. Assume that over $K$ frames there
+%are $M$ total parameter sets. In this context we will consider them as nodes in
+%a graph. We define the vector $\BS{c} \in \mathbb{R}^{M^2}$
+%where the entry $\BS{c}_{i + Mj} = \mathcal{D} \left( \theta_{i}, \theta_{j}
+%\right)$. If we have a set of connections $\Gamma_{i,j}$ we can calculate the
+%total cost of these connections by defining the vector
+%\[
+%    \BS{x}_{i + Mj} = \begin{cases}
+%        1 & \text{there is a connection between }i\text{ and }j\\
+%        0 & \text{otherwise}
+%    \end{cases}
+%\]
+%and then forming the inner product
+%\[
+%    c_{\text{total}}=\left\langle \BS{c},\BS{x} \right\rangle
+%\]
+%Note that a node cannot be connected to itself. The question is how to find
+%$\BS{x}^{\ast}$ so that $c_{\text{total}}$ is minimized. How do we
+%constrain $\BS{x}$ to give us a solution to the partial tracking
+%problem? Let us consider an example.
+%
+%In Figure~\ref{plot:simple_graph} we have an example of a simple graph or
+%lattice. Such a graph represents a plausible partial tracking situation:
+%vertically aligned nodes are parameter sets estimated from the same analysis
+%frame and we would like to connect these parameter sets between frames. The
+%numbers are indices of nodes in the graph and the edges (possible connections) between
+%them are indicated by lines. Imagine that we would like to
+%find the two shortest paths. We will now examine the resulting paths from two
+%algorithms using different criteria for shortness.
+%
+%In Figure~\ref{plot:simple_graph_greedy_paths} we find the paths using an
+%algorithm similar to Algorithms~\ref{alg:mq_peak_match} but search instead over a
+%tensor of distances $C \in \mathbb{R}^{3 \times 4 \times 2}$ whose entry
+%$C_{i,j,k}$ represents the cost of travelling on the path connecting the $i$th
+%node in layer 0, the $j$th node in layer 1 and the $k$th node in layer 2. This
+%cost is the sum of the Euclidean distances giving the lengths of the
+%connections. This is the greedy method of searching for the best paths whose
+%optimality criterion is to find the set of best paths containing the absolute
+%best path. We see in Figure~\ref{plot:simple_graph_greedy_paths} that the
+%absolute shortest path, $1 \rightarrow 4 \rightarrow 8$, is discovered, followed
+%by the second shortest path not using the nodes of the first path, $2
+%\rightarrow 5 \rightarrow 7$.
+%
+%\begin{figure}[!t]
+%    \centering
+%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex.eps}}
+%    \CaptionWithTitle{%
+%        \input{plots/small_graph_ex.txt}%
+%    }{\label{plot:simple_graph}}
+%\end{figure}
+%
+%\begin{figure}[!t]
+%    \centering
+%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_greedy_paths.eps}}
+%    \CaptionWithTitle{%
+%        \input{plots/small_graph_ex_greedy_paths.txt}%
+%    }{\label{plot:simple_graph_greedy_paths}}
+%\end{figure}
+%
+%\subsection{$L$ shortest paths via linear programming}
+%
+%To find a set of paths minimizing the total cost, we instead search for total
+%solutions $\BS{x}$ that describe all paths in the graph. Assume for now
+%that we can guarantee that the entries of $\BS{x}$ will be either 0 or
+%1. In order to simplify the indexing in this section, we denote the number of
+%nodes in each frame as $N_{k}$ ($M = \sum_{l=0}^{K-1} N_{k}$). To find a set of constraints for our search, we consider the structure of a
+%valid solution $\BS{x}^{\ast}$. To maintain that paths not overlap, a
+%valid solution's interior nodes (those not in the first or last frame) are only allowed to have one edge entering ---
+%coming from a node in a previous frame --- and one edge leaving
+%--- going to a node in a successive frame. To translate this into a
+%constraint, consider the node $i$ and its possible $R_{i}$ successive connecting
+%nodes $j_{0} \dotsc j_{R_{i}-1}$. Define the vector\footnote{The superscript s
+%stands for ``successive''.}
+%\[
+%    a^{\text{s},i}_{i + Mj_{r}} = \begin{cases}
+%        1 & \forall j_{r} \in \left[ j_{0} \dotsc j_{R_{i}-1} \right] \\
+%        0 & \text{otherwise}
+%    \end{cases}
+%\]
+%As all the entries of $\BS{x}$ are either 0 or 1, we have
+%\[
+%    0 \leq \left\langle \BS{a}^{\text{s},i}, \BS{x} \right\rangle \leq 1
+%\]
+%so we can make this a constraint to ensure that a node has at most one path
+%leaving. Similarly, if we consider the node $j$ and its possible $R_{j}$ previous connecting
+%nodes $i_{0} \dotsc i_{R_{j}-1}$, the vector\footnote{The superscript q
+%stands for ``previous''.}
+%\[
+%    a^{\text{q},j}_{i_{r} + Mj} \begin{cases}
+%        1 & \forall i_{r} \in \left[ i_{0} \dotsc i_{R_{j}-1} \right] \\
+%        0 & \text{otherwise}
+%    \end{cases}
+%\]
+%constrains that node $j$ have only one path entering through the constraint
+%\[
+%    0 \leq \left\langle \BS{a}^{\text{q},j} , \BS{x} \right\rangle \leq 1
+%\]
+%A node on a path will also have an edge entering and an edge leaving. To
+%translate this into a constraint, we define a vector that counts the number of
+%edges entering a node and subtracts then the number of edges leaving a node. The
+%result should always be 0 for an equal number of edges entering and exiting a
+%node. If $r$ is the index of the node considered, the vector is simply
+%\footnote{The superscript b stands for ``balanced''.}
+%\[
+%    \BS{a}^{\text{b},r} = \BS{a}^{\text{q},r} -
+%    \BS{a}^{\text{s},r}
+%\]
+%and the constraint
+%\[
+%    \left\langle \BS{a}^{\text{b},r}, \BS{x} \right\rangle = 0
+%\]
+%Finally we want to constrain that there be only $L$ paths. We do this by
+%noticing that if this is true, there will be $L$ edges between frames $k$ and
+%$k+1$. We constrain the number of paths going from edges
+%$\Gamma_{k}$ in frame $k$ to $\Gamma_{k+1}$ by forming the vector
+%\footnote{The superscript c stands for ``connections''.}
+%\[
+%    \BS{a}^{\text{c},k} = \sum_{j \in \Gamma_{k}}
+%    \BS{a}^{\text{s},j}
+%\]
+%and asserting the constraint
+%\[
+%    \left\langle \BS{a}^{\text{c},k} , \BS{x} \right\rangle = L
+%\]
+%The length of $\BS{x}$ is $M^{2}$ so the total size of all the
+%constraints is not insignificant, but most entries in the constraint vectors will
+%be 0 and therefore the resulting constraint matrices very sparse, so sparse
+%linear algebra routines can be used in computations. Furthermore, the
+%$\BS{a}^{\text{b}}$ and $\BS{a}^{\text{c}}$ constraints are derived from
+%$\BS{a}^{\text{q}}$ and $\BS{a}^{\text{s}}$, so only the latter need to be
+%stored.
+%
+%\begin{figure}[!t]
+%    \centering
+%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_lp_paths.eps}}
+%    \CaptionWithTitle{%
+%        \input{plots/small_graph_ex_lp_paths.txt}%
+%    }{\label{plot:simple_graph_lp_paths}}
+%\end{figure}
+%
+%The complete \textit{linear program (LP)} solving the $L$ shortest paths problem is then
+%\[
+%    \min_{\BS{x}} \left\langle \BS{c}, \BS{x} \right\rangle
+%\]
+%subject to
+%\[
+%    \BS{0} \leq
+%    \begin{bmatrix}
+%        \BS{A}_{\text{s}} \\
+%        \BS{A}_{\text{q}}
+%    \end{bmatrix} \BS{x}
+%    \leq \BS{1}
+%\]
+%\[
+%    \begin{bmatrix}
+%        \BS{A}_{\text{b}} \\
+%        \BS{A}_{\text{c}}
+%    \end{bmatrix}
+%    \BS{x}
+%    =
+%    \begin{bmatrix}
+%        \BS{0} \\
+%        L\BS{1}
+%    \end{bmatrix}
+%\]
+%\[
+%    \BS{0} \leq \BS{x} \leq \BS{1}
+%\]
+%where $\BS{A}_{\text{s}}$ is the matrix with
+%$\BS{a}^{\text{s},m}$ as its rows for $m \in [0 \dotsc M-1]$ and
+%$\BS{A}_{\text{q}}$ is the matrix with $\BS{a}^{\text{q},m}$ as
+%its rows, etc.
+%
+%The solution of the two best paths using the LP formulation
+%is shown in Figure~\ref{plot:simple_graph_lp_paths} and a comparison of the
+%total costs is shown in Table~\ref{tab:greedy_lp_cost_compare}
+%
+%\begin{table}[!b]
+%    \caption{\label{tab:greedy_lp_cost_compare} Comparison of total costs in
+%    Figure~\ref{plot:simple_graph_lp_paths}}
+%    \begin{center}
+%        \begin{tabular}{c c}
+%            Greedy & LP \\
+%            \hline
+%            \input{plots/small_graph_ex_greedy_cost.txt} &
+%            \input{plots/small_graph_ex_lp_cost.txt} \\
+%        \end{tabular}
+%    \end{center}
+%\end{table}
+%
+%The LP formulation is inspired by a multiple object tracking algorithm for video
+%\cite{jiang2007linear}. A proof that the solution $\BS{x}^{\ast}$ will
+%have entries equal to either $0$ or $1$ can be found in
+%\cite[q.~167]{parker1988discrete}. The theoretical computational complexity of
+%the linear program is polynomial in the number of variables, see
+%\cite{karmarkar1984new} for a proof and the demonstration of a fast algorithm
+%for finding its solution. In practice, to extract paths from the solution, we do
+%not test equality with $0$ or $1$ but rather test if the solution vector's
+%values are greater than some threshold. 
+%
 \subsection{Complexity}
@@
 the Viterbi algorithm for finding the single best path through a trellis whose
-$h$th frame has $\binom{N_{h}}{L}\binom{N_{h+1}}{L}L!$ connections where $N_{h}$
-and $N_{h+1}$ are the number of nodes in two consecutive frames of the original
+$k$th frame has $\binom{N_{k}}{L}\binom{N_{k+1}}{L}L!$ connections where $N_{k}$
+and $N_{k+1}$ are the number of nodes in two consecutive frames of the original
 lattice. Therefore, assuming a constant number $N$ of nodes in each frame, its
@@
 We compare the greedy and LP based methods for peak matching on a synthetic
-signal. The signal is composed of $K=6$ chirps of constant amplitude, the $k$th
+signal. The signal is composed of $Q=6$ chirps of constant amplitude, the $q$th
 chirp $s$ at sample $n$ described by the equation
 \[
-    s_{k}(n) = \exp(j(\phi_{k} + \omega_{k}n +
-    \frac{1}{2} \psi_{k} n^{2}))
+    s_{q}(n) = \exp(j(\phi_{q} + \omega_{q}n +
+    \frac{1}{2} \psi_{q} n^{2}))
 \]
@@
 \begin{table}[!b]
-    \caption{Parameters of $k$th chirp. $f_{0}$ and $f_{1}$ are the initial and
+    \caption{Parameters of $q$th chirp. $\nu_{0}$ and $\nu_{1}$ are the initial and
     final frequency of the chirp in Hz. \label{tab:ptrackexamplechirpparams}}
@@
         \begin{tabular}{l c c c c c}
-            $k$ & $\phi_{k}$ & $\omega_{k}$ & $\psi_{k}$ & $f_{0}$ & $f_{1}$ \\
+            $q$ & $\phi_{q}$ & $\omega_{q}$ & $\psi_{q}$ & $\nu_{0}$ & $\nu_{1}$ \\
             \hline
@@
 (DDM) to estimate the
-local chirp parameters, the $i$th set of parameters in frame $h$ denoted
-$\theta_{i}^{h} = \left\{ \phi_{i}^{h} , \omega_{i}^{h} , \psi_{i}^{h}
+local chirp parameters, the $i$th set of parameters in frame $k$ denoted
+$\theta_{i}^{k} = \left\{ \phi_{i}^{k} , \omega_{i}^{k} , \psi_{i}^{k}
 \right\}$ (the atoms used by the DDM are generated from 4-term continuous
@@
 \[
-    \mathcal{D}_{\text{pr.}} \left( \theta_{i}^{h},
-    \theta_{j}^{h+1} \right) = \left( \omega_{i}^{h} +
-    \psi_{i}^{h} H - \omega_{j}^{h+1} \right)
+    \mathcal{D}_{\text{pr.}} \left( \theta_{i}^{k},
+    \theta_{j}^{k+1} \right) = \left( \omega_{i}^{k} +
+    \psi_{i}^{k} H - \omega_{j}^{k+1} \right)
 \]
-which is the error in predicting $j$th frequency in frame $h+1$ from the $i$th
-parameters in frame $h$. For the greedy method, the search for partial paths is
+which is the error in predicting $j$th frequency in frame $k+1$ from the $i$th
+parameters in frame $k$. For the greedy method, the search for partial paths is
 restricted to one frame ahead like in \cite{mcaulay1986speech}, otherwise the

### 2017-04-17 lp_path_small.py

@@ -1,0 +1,169 @@
+import numpy as np
+import itertools as it
+import cvxopt
+import matplotlib.pyplot as plt
+import lpmisc
+
+def print_0_1_array(x):
+    """
+    Prints an array containing only 0s and 1s in a consise way.
+    """
+    for row in x:
+        s=""
+        for col in row:
+            s += "%2.0f" % (col,)
+        print s
+
+def get_L_best_paths_mats(i_frames,i_vals,dfunc,dmax,L):
+
+    """
+    i_frames:
+        indices in each frame
+    i_vals:
+        values for each index such that the value of an index can be looked up
+        as i_vals[idx]
+    dfunc:
+        function that accepts two entries from i_vals and gives distance between
+        them
+    dmax:
+        the maximum tolerated distance
+    L:
+        the number of paths to find
+
+    returns:
+        (c,G,h,A,b,M,i_pairs,i_costs)
+
+        c:
+            cost vector
+        G: 
+            inequality constraint matrix
+        h:
+            inequality constraint vector
+        A:
+            equality constraint matrix
+        b:
+            equality constraint vector
+        M:
+            number of pairs considered
+        i_pairs:
+            the pairs of indices
+        i_costs:
+            the cost of each connection between the respective pairs
+
+    TODO: Only works with simplex method.
+    """
+
+    # number of frames
+    F=len(i_frames)
+
+    # compute index pairs
+    i_pairs=list(it.imap(lambda x,y : list(it.product(x,y)), i_frames[:-1], i_frames[1:]))
+    i_pairs=reduce(lambda x,y : x+y, i_pairs)
+    fv_dict=dict()
+    i_all=reduce(lambda x,y : x+y, i_frames)
+    for idx,val in zip(i_all,i_vals):
+        fv_dict[idx]=val
+
+    # compute costs for each pair
+    i_costs=[float("inf") for _ in i_pairs]
[…]

### 2017-04-17 lp_path_small_no_redund.py

@@ -1,0 +1,191 @@
+import numpy as np
+import itertools as it
+import cvxopt
+import matplotlib.pyplot as plt
+import lpmisc
+import string
+from numpy import linalg
+
+def print_0_1_array(x,remove_0s=False):
+    """
+    Prints an array containing only 0s and 1s in a consise way.
+    """
+    for row in x:
+        s=""
+        for col in row:
+            s += "%2.0f" % (col,)
+        if (remove_0s):
+            s=s.translate(string.maketrans("0"," "))
+        print s
+
+def get_L_best_paths_mats(i_frames,i_vals,dfunc,dmax,L):
+
+    """
+    i_frames:
+        indices in each frame
+    i_vals:
+        values for each index such that the value of an index can be looked up
+        as i_vals[idx]
+    dfunc:
+        function that accepts two entries from i_vals and gives distance between
+        them
+    dmax:
+        the maximum tolerated distance
+    L:
+        the number of paths to find
+
+    returns:
+        (c,G,h,A,b,M,i_pairs,i_costs)
+
+        c:
+            cost vector
+        G: 
+            inequality constraint matrix
+        h:
+            inequality constraint vector
+        A:
+            equality constraint matrix
+        b:
+            equality constraint vector
+        M:
+            number of pairs considered
+        i_pairs:
+            the pairs of indices
+        i_costs:
+            the cost of each connection between the respective pairs
+
+        Works with both simlpex and interior-point methods.
+    """
+
+    # number of frames
+    F=len(i_frames)
+
+    # compute index pairs
+    i_pairs=list(it.imap(lambda x,y : list(it.product(x,y)), i_frames[:-1], i_frames[1:]))
+    i_pairs=reduce(lambda x,y : x+y, i_pairs)
+    fv_dict=dict()
+    i_all=reduce(lambda x,y : x+y, i_frames)
+    for idx,val in zip(i_all,i_vals):
[…]

### 2017-04-17 lp_path_test.py

@@ -162,11 +162,11 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     # and its vector
     h=np.vstack((bs,bp,0*bs,0*bp,v1,0*v1))
     # Build equality contraint matrix
-    A=np.vstack((Ab_,Ac))#,Anoc))#,Anic))
-    b=np.vstack((bb,bc))#,bnoc))#,bnic))
+    A=np.vstack((Ab_,Ac))
+    b=np.vstack((bb,bc))
     return (G,h,A,b,M)
 
-N_frames = 15 
+N_frames = 10 
 N_pts_per_frame = 5
 x_pts=np.add.outer(np.arange(N_frames),np.zeros(N_pts_per_frame)).flatten()
 y_pts=np.random.uniform(-1,1,N_frames*N_pts_per_frame)

### 2017-04-17 lp_path_test_lp_extract_path.py

@@ -126,36 +126,8 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
         Ac_[f,:]=np.sum(As_[fpts,:],axis=0) # sum along rows
     for f,fpts in enumerate(pts_per_frame[:-1]):
         Ac[f,:]=np.sum(As[fpts,:],axis=0) # sum along rows
-    # in last frame there are only incoming connections so use these to count
-    #Ac[-1,:]=np.sum(Ap[-n_pts_per_frame[-1],:],axis=0)
     # vector
     bc=L*np.ones((F-1,1))
-    # Number of outgoing connections to non-contiguous frames constrained to 0
-    Anoc=np.zeros((sum(n_pts_per_frame[:-2]),M*M))
-    r=0
-    for i in xrange(len(pts_per_frame)-2):
-        fpts=pts_per_frame[i]
-        if (i == (len(pts_per_frame)-3)):
-            rest_pts=pts_per_frame[-1]
-        else:
-            rest_pts=reduce(lambda x,y : x+y, pts_per_frame[i+2:]) # note this performs list concatenation
-        for fpt in fpts:
-            Anoc[r,M*fpt + np.array(rest_pts)]=1
-            r+=1
-    bnoc=np.zeros((Anoc.shape[0],1))
-    # Number of incoming connections to non-contiguous frames constrained to 0
-    Anic=np.zeros((sum(n_pts_per_frame[2:]),M*M))
-    r=0
-    for i in xrange(len(pts_per_frame)-2):
-        fpts=pts_per_frame[i+2]
-        if (i == 0):
-            rest_pts=pts_per_frame[0]
-        else:
-            rest_pts=reduce(lambda x,y : x+y, pts_per_frame[i+2:])
-        for fpt in fpts:
-            Anic[r,M*np.array(rest_pts) + fpt]=1
-            r+=1
-    bnic=np.zeros((Anic.shape[0],1))
 
     # Also need 0 <= x <= 1
     I=np.eye(M*M)
@@ -167,10 +139,17 @@ def get_L_best_paths_mats(c,n_pts_per_frame,L):
     G=np.vstack((G,np.hstack((I,-I,-I))))
[…]

### 2017-04-17 lpmisc.py

@@ -1,0 +1,44 @@
+# Miscellaneous LP stuff
+import cvxopt
+import numpy as np
+
+def check_if_redundant(A,b,s,t):
+    """
+    Given system of linear inequalities A*x <= b determine if s^T*x <= t is a
+    redundant inequality. Returns True if redundant, else False.
+
+    A,b,s must be of type numpy.ndarray and t must be a float.
+    s must be row vector
+
+    """
+    G=np.vstack((A,s))
+    h=np.vstack((b,np.array([[t+1]])))
+    s_=cvxopt.matrix(s.reshape((s.shape[1],1)))
+    G_=cvxopt.sparse(cvxopt.matrix(G))
+    h_=cvxopt.matrix(h)
+    sol=cvxopt.solvers.lp(-1*s_,G_,h_,solver='glpk')
+    #print 'primal objective %f' % (sol['primal objective'],)
+    #print 'sol[x]: '
+    #print sol['x']
+    # primal objective negated because lp solver can only minimize
+    return -sol['primal objective'] <= t
+
+def check_if_redundant_test():
+    A=np.array([[1,1],[-1,1]])
+    # this is redundant
+    s=np.array([[1./3,1/2.]])
+    b=np.array([1,1]).reshape((2,1))
+    t=1.
+    if check_if_redundant(A,b,s,t):
+        print 'redundant'
+    else:
+        print 'not redundant'
+    A=np.array([[1,1],[-1,1]])
+    # this is not redundant
+    s=np.array([[1./3,2.]])
+    b=np.array([1,1]).reshape((2,1))
+    t=1.
+    if check_if_redundant(A,b,s,t):
+        print 'redundant'
+    else:
+        print 'not redundant'

### 2017-04-18 paper/paper.tex
Added section on computational complexity

@@
 Indeed, we have $\BS{0} \leq \BS{x} \leq \BS{1}$, therefore we will always have
-$\BS{A}^{\text{I}}\BS{x} \geq 0$ and $\BS{A}^{\text{I}}\BS{x} \geq 0$.
+$\BS{A}^{\text{I}}\BS{x} \geq 0$ and $\BS{A}^{\text{O}}\BS{x} \geq 0$.
 Furthermore, all but the last row of (\ref{eq:cxnlcon}) can be seen as
@@
 The complete LP to find the $L$ best disjoint paths through a lattice described
-by node connections $\rho$ is
+by node connections $\rho$ is then
 \[
@@
 \end{equation}
+where $\BS{I}$ is the identity matrix.
 
-% TODO: move to complexity
+\section{Complexity}
 
-%\section{An optimal method \label{sec:lppathsearch}}
-%
-%There is a way to find a set of paths over multiple frames ($K > 2$) having the
-%lowest total cost if
-%we restrict the search to exactly $L$ paths. Instead of indexing parameters by
-%their frame number $k$, we make $k$ part of the parameter set so that it can be
-%used by the distance function $\mathcal{D}$. Assume that over $K$ frames there
-%are $M$ total parameter sets. In this context we will consider them as nodes in
-%a graph. We define the vector $\BS{c} \in \mathbb{R}^{M^2}$
-%where the entry $\BS{c}_{i + Mj} = \mathcal{D} \left( \theta_{i}, \theta_{j}
-%\right)$. If we have a set of connections $\Gamma_{i,j}$ we can calculate the
-%total cost of these connections by defining the vector
-%\[
-%    \BS{x}_{i + Mj} = \begin{cases}
-%        1 & \text{there is a connection between }i\text{ and }j\\
-%        0 & \text{otherwise}
-%    \end{cases}
-%\]
-%and then forming the inner product
-%\[
-%    c_{\text{total}}=\left\langle \BS{c},\BS{x} \right\rangle
-%\]
-%Note that a node cannot be connected to itself. The question is how to find
-%$\BS{x}^{\ast}$ so that $c_{\text{total}}$ is minimized. How do we
-%constrain $\BS{x}$ to give us a solution to the partial tracking
-%problem? Let us consider an example.
-%
-%In Figure~\ref{plot:simple_graph} we have an example of a simple graph or
-%lattice. Such a graph represents a plausible partial tracking situation:
-%vertically aligned nodes are parameter sets estimated from the same analysis
-%frame and we would like to connect these parameter sets between frames. The
-%numbers are indices of nodes in the graph and the edges (possible connections) between
-%them are indicated by lines. Imagine that we would like to
-%find the two shortest paths. We will now examine the resulting paths from two
-%algorithms using different criteria for shortness.
-%
-%In Figure~\ref{plot:simple_graph_greedy_paths} we find the paths using an
-%algorithm similar to Algorithms~\ref{alg:mq_peak_match} but search instead over a
-%tensor of distances $C \in \mathbb{R}^{3 \times 4 \times 2}$ whose entry
-%$C_{i,j,k}$ represents the cost of travelling on the path connecting the $i$th
-%node in layer 0, the $j$th node in layer 1 and the $k$th node in layer 2. This
-%cost is the sum of the Euclidean distances giving the lengths of the
-%connections. This is the greedy method of searching for the best paths whose
-%optimality criterion is to find the set of best paths containing the absolute
-%best path. We see in Figure~\ref{plot:simple_graph_greedy_paths} that the
-%absolute shortest path, $1 \rightarrow 4 \rightarrow 8$, is discovered, followed
-%by the second shortest path not using the nodes of the first path, $2
-%\rightarrow 5 \rightarrow 7$.
-%
-%\begin{figure}[!t]
-%    \centering
-%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex.eps}}
-%    \CaptionWithTitle{%
-%        \input{plots/small_graph_ex.txt}%
-%    }{\label{plot:simple_graph}}
-%\end{figure}
-%
-%\begin{figure}[!t]
-%    \centering
-%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_greedy_paths.eps}}
-%    \CaptionWithTitle{%
-%        \input{plots/small_graph_ex_greedy_paths.txt}%
-%    }{\label{plot:simple_graph_greedy_paths}}
-%\end{figure}
-%
-%\subsection{$L$ shortest paths via linear programming}
-%
-%To find a set of paths minimizing the total cost, we instead search for total
-%solutions $\BS{x}$ that describe all paths in the graph. Assume for now
-%that we can guarantee that the entries of $\BS{x}$ will be either 0 or
-%1. In order to simplify the indexing in this section, we denote the number of
-%nodes in each frame as $N_{k}$ ($M = \sum_{l=0}^{K-1} N_{k}$). To find a set of constraints for our search, we consider the structure of a
-%valid solution $\BS{x}^{\ast}$. To maintain that paths not overlap, a
-%valid solution's interior nodes (those not in the first or last frame) are only allowed to have one edge entering ---
-%coming from a node in a previous frame --- and one edge leaving
-%--- going to a node in a successive frame. To translate this into a
-%constraint, consider the node $i$ and its possible $R_{i}$ successive connecting
-%nodes $j_{0} \dotsc j_{R_{i}-1}$. Define the vector\footnote{The superscript s
-%stands for ``successive''.}
-%\[
-%    a^{\text{s},i}_{i + Mj_{r}} = \begin{cases}
-%        1 & \forall j_{r} \in \left[ j_{0} \dotsc j_{R_{i}-1} \right] \\
-%        0 & \text{otherwise}
-%    \end{cases}
-%\]
-%As all the entries of $\BS{x}$ are either 0 or 1, we have
-%\[
-%    0 \leq \left\langle \BS{a}^{\text{s},i}, \BS{x} \right\rangle \leq 1
-%\]
-%so we can make this a constraint to ensure that a node has at most one path
-%leaving. Similarly, if we consider the node $j$ and its possible $R_{j}$ previous connecting
-%nodes $i_{0} \dotsc i_{R_{j}-1}$, the vector\footnote{The superscript q
-%stands for ``previous''.}
-%\[
-%    a^{\text{q},j}_{i_{r} + Mj} \begin{cases}
-%        1 & \forall i_{r} \in \left[ i_{0} \dotsc i_{R_{j}-1} \right] \\
-%        0 & \text{otherwise}
-%    \end{cases}
-%\]
-%constrains that node $j$ have only one path entering through the constraint
-%\[
-%    0 \leq \left\langle \BS{a}^{\text{q},j} , \BS{x} \right\rangle \leq 1
-%\]
-%A node on a path will also have an edge entering and an edge leaving. To
-%translate this into a constraint, we define a vector that counts the number of
-%edges entering a node and subtracts then the number of edges leaving a node. The
-%result should always be 0 for an equal number of edges entering and exiting a
-%node. If $r$ is the index of the node considered, the vector is simply
-%\footnote{The superscript b stands for ``balanced''.}
-%\[
-%    \BS{a}^{\text{b},r} = \BS{a}^{\text{q},r} -
-%    \BS{a}^{\text{s},r}
-%\]
-%and the constraint
-%\[
-%    \left\langle \BS{a}^{\text{b},r}, \BS{x} \right\rangle = 0
-%\]
-%Finally we want to constrain that there be only $L$ paths. We do this by
-%noticing that if this is true, there will be $L$ edges between frames $k$ and
-%$k+1$. We constrain the number of paths going from edges
-%$\Gamma_{k}$ in frame $k$ to $\Gamma_{k+1}$ by forming the vector
-%\footnote{The superscript c stands for ``connections''.}
-%\[
-%    \BS{a}^{\text{c},k} = \sum_{j \in \Gamma_{k}}
-%    \BS{a}^{\text{s},j}
-%\]
-%and asserting the constraint
-%\[
-%    \left\langle \BS{a}^{\text{c},k} , \BS{x} \right\rangle = L
-%\]
-%The length of $\BS{x}$ is $M^{2}$ so the total size of all the
-%constraints is not insignificant, but most entries in the constraint vectors will
-%be 0 and therefore the resulting constraint matrices very sparse, so sparse
-%linear algebra routines can be used in computations. Furthermore, the
-%$\BS{a}^{\text{b}}$ and $\BS{a}^{\text{c}}$ constraints are derived from
-%$\BS{a}^{\text{q}}$ and $\BS{a}^{\text{s}}$, so only the latter need to be
-%stored.
-%
-%\begin{figure}[!t]
-%    \centering
-%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_lp_paths.eps}}
-%    \CaptionWithTitle{%
-%        \input{plots/small_graph_ex_lp_paths.txt}%
-%    }{\label{plot:simple_graph_lp_paths}}
-%\end{figure}
-%
-%The complete \textit{linear program (LP)} solving the $L$ shortest paths problem is then
-%\[
-%    \min_{\BS{x}} \left\langle \BS{c}, \BS{x} \right\rangle
-%\]
-%subject to
-%\[
-%    \BS{0} \leq
-%    \begin{bmatrix}
-%        \BS{A}_{\text{s}} \\
-%        \BS{A}_{\text{q}}
-%    \end{bmatrix} \BS{x}
-%    \leq \BS{1}
-%\]
-%\[
-%    \begin{bmatrix}
-%        \BS{A}_{\text{b}} \\
-%        \BS{A}_{\text{c}}
-%    \end{bmatrix}
-%    \BS{x}
-%    =
-%    \begin{bmatrix}
-%        \BS{0} \\
-%        L\BS{1}
-%    \end{bmatrix}
-%\]
-%\[
-%    \BS{0} \leq \BS{x} \leq \BS{1}
-%\]
-%where $\BS{A}_{\text{s}}$ is the matrix with
-%$\BS{a}^{\text{s},m}$ as its rows for $m \in [0 \dotsc M-1]$ and
-%$\BS{A}_{\text{q}}$ is the matrix with $\BS{a}^{\text{q},m}$ as
-%its rows, etc.
-%
-%The solution of the two best paths using the LP formulation
-%is shown in Figure~\ref{plot:simple_graph_lp_paths} and a comparison of the
-%total costs is shown in Table~\ref{tab:greedy_lp_cost_compare}
-%
-%\begin{table}[!b]
-%    \caption{\label{tab:greedy_lp_cost_compare} Comparison of total costs in
-%    Figure~\ref{plot:simple_graph_lp_paths}}
-%    \begin{center}
-%        \begin{tabular}{c c}
-%            Greedy & LP \\
-%            \hline
-%            \input{plots/small_graph_ex_greedy_cost.txt} &
-%            \input{plots/small_graph_ex_lp_cost.txt} \\
-%        \end{tabular}
-%    \end{center}
-%\end{table}
-%
-%The LP formulation is inspired by a multiple object tracking algorithm for video
-%\cite{jiang2007linear}. A proof that the solution $\BS{x}^{\ast}$ will
-%have entries equal to either $0$ or $1$ can be found in
-%\cite[q.~167]{parker1988discrete}. The theoretical computational complexity of
-%the linear program is polynomial in the number of variables, see
-%\cite{karmarkar1984new} for a proof and the demonstration of a fast algorithm
-%for finding its solution. In practice, to extract paths from the solution, we do
-%not test equality with $0$ or $1$ but rather test if the solution vector's
-%values are greater than some threshold. 
-%
-\subsection{Complexity}
+% TODO: Memory complexity
+
+Here we will compare the complexity of the LP formulation of the best $L$ paths
+search to the greedy McAulay-Quatieri method as well a combinatorial algorithm
+proposed in \cite{wolf1989finding}.
+
+Assuming the same number of nodes $N$ in each frame of the lattice, the 
+search for the $l$th best path in the generalized McAulay-Quatieri
+algorithm ($0 \leq l < L$) requires a search over $(N-l)^{K}$ possible paths.
 
@@
 solution to the $L$-best paths problem proposed in \cite{wolf1989finding}. The
-complexity of our algorithm is different.  Assuming we
-use the algorithm in \cite{karmarkar1984new} to solve the LP, our program has a
-complexity of $O(M^{7}B^{2})$ where $M$ is the number of nodes (parameter sets)
-and $B$ is the number of bits used to represent each number in the input. The
 complexity of the algorithm by Wolf in \cite{wolf1989finding} is equivalent to
@@
 lattice. Therefore, assuming a constant number $N$ of nodes in each frame, its
-complexity is $O((\binom{N}{L}^{2}L!)^{2}T)$. If there are few nodes in each
-frame and a small number of paths are searched, Wolf's formulation is superior
-as its complexity increases linearly with the number of frames in the lattice.
-On the other hand, if each frame has a large number of nodes or many paths are
-searched, the LP formulation is superior.  Informally we have found this to
-agree with reality --- both algorithms were tried when producing the figures in
-Section~\ref{sec:mq_lp_compare_chirp}.  Indeed the Wolf formulation took
-prohibitively long to compute when many paths were desired, as did the LP when
-many frames were considered.
+complexity is $O((\binom{N}{L}^{2}L!)^{2}K)$.
 
-In the special case that only 1 shortest path is searched the Viterbi algorithm
-\cite{forney1973viterbi} can be used that only requires on the order of $N^{2}T$
-calculations \cite{rabiner1989tutorial} where $N$ is the number of nodes in each
-frame and $T$ is the number of frames (assuming the same number of nodes in each
-frame).
+The complexity of the algorithm presented here is polynomial in the number of
+variables (the size of $\BS{x}$).  Assuming we use the algorithm in
+\cite{karmarkar1984new} to solve the LP, our program has a complexity of
+$O(P^{3.5}B^{2})$ where $B$ is the number of bits used to represent each number
+in the input.  However, this bound is conservative considering the reported
+complexity of modern algorithms.
+
+For instance, the complexity of a log-barrier interior-point method is dominated
+by solving the system of equations
+\begin{equation}
+    \label{eq:kkt}
+    \begin{bmatrix}
+        -\BS{D}\BS{G}^{T}\BS{G} & \BS{A}^{T} \\
+        \BS{A} & \BS{0}
+    \end{bmatrix}
+    \begin{bmatrix}
+        \BS{u} \\
+        \BS{v}
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+        t\cLP + \BS{A}^{T}\BS{d} \\
+        \BS{0}
+    \end{bmatrix}
+\end{equation}
+some $10$s of times \cite[p.~590]{boyd2004convex}. 
+Each iteration then takes ${\frac{2}{3}((K-1)N^{2} + (K-2)N)^{3}}$ flops (floating-point
+operations) to solve ($\ref{eq:kkt}$) using a standard $LU$-decomposition
+\cite[p.~98]{golub1996matrix}. As
+$\BS{D}$ is a diagonal matrix, if
+the number of nodes in each frame is $N$ for all frames, then
+$\BS{D}\BS{G}^{T}\BS{G}$ will be a block-diagonal matrix made up of $K-1$ blocks
+$\BS{B}_k \in \mathbb{R}^{N^{2}\times N^{2}}$. The system can then be solved in
+\begin{multline*}
+    \frac{2}{3}(K-1)N^{6} + 2(K-2)(K-1)N^{5} + \\
+    2(K-2)^{2}(K-1)N^{4} + \frac{2}{3}(K-2)^{3}N^{3}
+\end{multline*}
+flops \cite[p.~675]{boyd2004convex}; this complexity is without exploiting the
+sparsity of $\BS{A}$ nor the structure of $\BS{B}_k = \BS{D}_{k}\BS{C}$ --- the product
+of some diagonal matrix $\BS{D}_{k}$ with an unchanging symmetric matrix
+$\BS{C}$.
 

### 2017-04-18 paper/paper.tex
Added memory complexity.

@@
 \begin{equation}
+    \label{eq:lpprogfull}
     \BS{A}\BS{x} =
@@
 
+\section{Memory complexity}
+
+To simplify notation, in this section we assume there are $N$ nodes in each
+frame of the lattice.
+
+Although the matrices involved in (\ref{eq:lpprogfull}) are large, only a small
+fraction of their values are non-zero. As stated above, the number of variables in $\BS{x}$ is
+$P = (K-1)N^{2}$. Even though matrices $\BS{A}^{\text{I}}, \BS{A}^{\text{O}} \in
+\mathbb{R}^{N(K-1) \times P}$, each contains only $P$ non-zero
+entries.  $\BS{A}^{\text{B}} \in \mathbb{R}^{N(K-1) \times P}$ but contains only
+$2N^{2}(K-2)$ non-zero entries while $\BS{A}^{\text{C}}_{K-2} \in \mathbb{R}^{P}$
+contains merely $N$. The $\BS{x} \geq \BS{0}$ constraint requires a matrix
+with $P$ non-zero entries. The total memory complexity is therefore $4P +
+2N^{2}(K-2)$ floating-point numbers.
+
 \section{Complexity}
-
-% TODO: Memory complexity
 

### 2017-04-19 bestpathslp.py
Starting to add example application
Also will compare with MQ greedy method.

@@ -1,0 +1,119 @@
+import numpy as np
+import itertools as it
+import cvxopt
+import matplotlib.pyplot as plt
+import lpmisc
+import string
+from numpy import linalg
+
+def get_lp_mats(i_frames,i_vals,dfunc,dmax,L):
+
+    """
+    i_frames:
+        indices in each frame
+    i_vals:
+        values for each index such that the value of an index can be looked up
+        as i_vals[idx]
+    dfunc:
+        function that accepts two entries from i_vals and gives distance between
+        them
+    dmax:
+        the maximum tolerated distance
+    L:
+        the number of paths to find
+
+    returns:
+        (c,G,h,A,b,M,i_pairs,i_costs)
+
+        c:
+            cost vector
+        G: 
+            inequality constraint matrix
+        h:
+            inequality constraint vector
+        A:
+            equality constraint matrix
+        b:
+            equality constraint vector
+        M:
+            number of pairs considered
+        i_pairs:
+            the pairs of indices
+        i_costs:
+            the cost of each connection between the respective pairs
+
+        Works with both simplex and interior-point methods.
+    """
+
+    # number of frames
+    F=len(i_frames)
+
+    # compute index pairs
+    i_pairs=list(it.imap(lambda x,y : list(it.product(x,y)), i_frames[:-1], i_frames[1:]))
+    i_pairs=reduce(lambda x,y : x+y, i_pairs)
+    fv_dict=dict()
+    i_all=reduce(lambda x,y : x+y, i_frames)
+    for idx,val in zip(i_all,i_vals):
+        fv_dict[idx]=val
+
+    # compute costs for each pair
+    i_costs=[float("inf") for _ in i_pairs]
+    for idx,pair in enumerate(i_pairs):
+        i,j=pair
+        i_costs[idx]=dfunc(i_vals[i],i_vals[j])
+
+    # filter excessive costs
+    fltr_v=[i_cost < dmax for i_cost in i_costs]
+    i_pairs=list(it.compress(i_pairs,fltr_v))
+    i_costs=list(it.compress(i_costs,fltr_v))
+
+    # number of pairs
+    M=len(i_pairs)
+
[…]

### 2017-04-20 bestpathslp.py
Added MQ best path search function and DDM decomposition.

@@ -5,6 +5,8 @@ import matplotlib.pyplot as plt
 import lpmisc
 import string
 from numpy import linalg
+import sigmod as sm
+import ddm
 
 def get_lp_mats(i_frames,i_vals,dfunc,dmax,L):
 
@@ -116,4 +118,101 @@ def get_lp_mats(i_frames,i_vals,dfunc,dmax,L):
     return (c,G,h,A,b,M,i_pairs,i_costs)
 
 def get_mq_sol(i_frames,i_vals,dfunc,dmax,L):
-    pass
+    """
+    i_frames:
+        indices in each frame. Must be contiguous and start at 0, e.g.,
+        [[0,1],[2,3,4],...]
+    i_vals:
+        values for each index such that the value of an index can be looked up
+        as i_vals[idx]
+    dfunc:
+        function that accepts two entries from i_vals and gives distance between
+        them
+    dmax:
+        the maximum tolerated distance
+    L:
+        the number of paths to find
+
+    returns (x,D)
+
+    x:
+        a list of lists of indices representing L best paths sorted from
+        shortest to longest
+    D:
+        the cost tensor for all the paths
+    """
+    dim_sizes=[len(d) for d in i_frames]
+    for dim_idcs,fr_idcs in zip(it.product(*map(xrange,dim_sizes)),it.product(*i_frames)):
+        vals_pairs=[(i_vals[i],
+            i_vals[j]) for i,j in zip(fr_idcs[:-1],fr_idcs[1:])]
+        D.itemset(dim_idcs,sum([dfunc(iv,jv) for iv,jv in vals_pairs]))
+    x=[]
+    all_dim_idcs=list(it.product(*map(xrange,dim_sizes)))
+    for j in xrange(L):
+        min_cost=float('inf')
+        min_idcs=None
+        for dim_idcs in all_dim_idcs:
+            if (D.item(dim_idcs) < min_cost):
+                min_cost = D.item(dim_idcs)
+                min_idcs = dim_idcs
+        if min_cost > dmax:
+            break
+        x.append(min_idcs)
+        all_dim_idcs.remove(min_idcs)
+    return x
+
+def estimate_ddm_decomp(x,
+                        Fs=16000,
+                        M=1024,
+                        H=256,
+                        wname='c1-nuttall-4',
+                        b_ddm_hz=150.,
+                        o_ddm_hz=75.,
[…]

### 2017-04-20 setup_pythonpath.sh

@@ -1,0 +1,1 @@
+export PYTHONPATH=../signal_modeling/:../signal_modeling/test/:../cont_win_comp/:$PYTHONPATH

### 2017-04-20 test/bestpathslp_test.py

@@ -1,0 +1,21 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import bestpathslp as bplp
+
+fname='/Users/mondaugen/Documents/sound/timit/TIMIT/TEST/DR1/FAKS0/SA1_your_dark.f64'
+x=np.fromfile(fname,dtype='float64')
+Fs=16000
+H=256
+a=bplp.estimate_ddm_decomp(x,H=H,th_ddm=0.,#10.**(-100./20),
+        Fs=Fs)
+fig,ax1=plt.subplots(1,1)
+h=0
+for a_ in a:
+    for a__ in a_:
+        f0_=np.imag(a__[1])/(2.*np.pi)*Fs
+        f1_=(np.imag(a__[1])+2.*np.imag(a__[2])*H)/(2.*np.pi)*Fs
+        t0_=h/float(Fs)
+        t1_=(h+H)/float(Fs)
+        ax1.plot([t0_,t1_],[f0_,f1_],c='k')
+    h+=H
+plt.show()

### 2017-04-20 test/bestpathslp_double_points_test.py
Trying out partial tracking of chirps with new algorithm
Seems a bit faster, which is good, but doesn't handle crossing well yet.

Trying to add 'doubles' in some frames so we can have multiple paths cross a node.

@@ -1,3 +1,5 @@
+# Try doubling up some points in the middle to see if this makes enough
+# room for all the paths
 import matplotlib.pyplot as plt
 import numpy as np
 import bestpathslp as bplp
@@ -52,8 +54,8 @@ for a_ in a_flt:
     for a__ in a_:
         f0_=np.imag(a__[1])/(2.*np.pi)*Fs
         f1_=(np.imag(a__[1])+2.*np.imag(a__[2])*H)/(2.*np.pi)*Fs
-        t0_=h/float(Fs)
-        t1_=(h+H)/float(Fs)
+        t0_=h/H#float(Fs)
+        t1_=(h+H)/H#float(Fs)
         ax1.plot([t0_,t1_],[f0_,f1_],c='k')
     h+=H
 
@@ -67,6 +69,15 @@ i_frames=[]
 # times at which corresponding points happen
 i_times=[]
 h=0
+
+# frames in which to double the points
+i_double=range(20,31)
+
+for i in i_double:
+    atlen=len(a_flt[i])
+    for j in xrange(atlen):
+        a_flt[i].append(a_flt[i][j].copy())
+
 for a_ in a_flt:
     i_frames.append(i_frames_[:len(a_)])
     i_times += [h for _ in xrange(len(a_))]
@@ -81,7 +92,7 @@ def dfunc(a,b):
 (c,G,h,A,b,M,i_pairs,i_costs)=bplp.get_lp_mats(i_frames,
                                                i_vals,
                                                dfunc,
-                                               0.15,
+                                               0.1,
                                                L)
 print 'max cost %f' % (max(i_costs),)
 print 'min cost %f' % (min(i_costs),)
@@ -100,8 +111,8 @@ for x_pt in zip(sol['x'],i_pairs):
     if x > 0.5:
         f0_=np.imag(i_vals[i][1])/(2.*np.pi)*Fs
         f1_=np.imag(i_vals[j][1])/(2.*np.pi)*Fs
-        t0_=i_times[i]/float(Fs)
-        t1_=i_times[j]/float(Fs)
+        t0_=i_times[i]/H#float(Fs)
+        t1_=i_times[j]/H#float(Fs)
         ax1.plot([t0_,t1_],[f0_,f1_],c='r')
 
 if (show_plot):

### 2017-04-21 paper/paper.tex
Just going with simple comparison
LP vs MQ. Looks pretty good, just gotta improve the plots and make the notation match in the paper.
Notably: MQ now rejects paths whose local cost is greater than threshold, in paper it was global cost
gotta change that.

@@
 % --------------------
-\title{PARTIAL TRACKING VIA LINEAR PROGRAMMING}
+\title{A linear programming approach to the tracking of partials}
 
@@
 \twoauthors
-  {Nicholas Esterer\sthanks{}}
-    {McGill University \\
-     Music Technology Area \\
-     Schulich School of Music, McGill University \\
+  {Nicholas Esterer}%\sthanks{}}
+    {Schulich School of Music, McGill University, \\
+     Music Technology Area \& CIRMMT \\
      555 Sherbrooke Street West \\
@@
      nicholas.esterer@mail.mcgill.ca}
-  {Philippe Depalle\sthanks{}}
-    {McGill University \\
-     Music Technology Area \\
-     Schulich School of Music, McGill University \\
+ {Philippe Depalle}%\sthanks{}}
+    {Schulich School of Music, McGill University, \\
+     Music Technology Area \& CIRMMT \\
      555 Sherbrooke Street West \\
@@
 \begin{abstract}
-    TODO
+    A new approach to the tracking of sinusoidal chirps using linear programming
+    is proposed. It is demonstrated that the classical algorithm of
+    \cite{mcaulay1986speech} is greedy and exhibits exponential complexity for
+    long searches. A linear programming (LP) formulation to find the best $L$ paths
+    in a lattice is described and its complexity is analysed. Finally it is
+    demonstrated that the new LP formulation outperforms the classical algorithm
+    in the tracking of sinusoidal chirps in high levels of noise --- both in
+    computational complexity and robustness.
 \end{abstract}
@@
 
-Typically the DTSTFT is computed for a block of contiguous samples, called a
-\textit{frame} and these frames are computed every $H$ samples, $H$ being the
-\textit{hop-size}. We will denote the $N_{k}$ sets of parameters at local maxima in
-frame $k$ as $\theta_0^{k}, \dotsc, \theta_{N_{k}-1}^{k}$ and the $N_{k+1}$ in frame $k+1$
-as $\theta_0^{k+1}, \dotsc, \theta_{N_{k+1}-1}^{k+1}$ where $k$ and $k+1$ refer to
+Typically the discrete time short-time Fourier transform (DTSTFT) is computed
+for a block of contiguous samples, called a \textit{frame} and these frames are
+computed every $H$ samples, $H$ being the \textit{hop-size}. We will denote the
+$N_{k}$ sets of parameters at local maxima in frame $k$ as $\theta_0^{k},
+\dotsc, \theta_{N_{k}-1}^{k}$ and the $N_{k+1}$ in frame $k+1$ as
+$\theta_0^{k+1}, \dotsc, \theta_{N_{k+1}-1}^{k+1}$ where $k$ and $k+1$ refer to
 adjacent frames. We are interested in paths that extend across $K$ frames where
@@
 $\BS{x}_{i}$ is the $i$th row or column of that vector depending on the
-orientation. The same notation is used for cartesian products, e.g., if $\alpha$
+orientation. The same notation is used for Cartesian products, e.g., if $\alpha$
 and $\beta$ are sets and $A =
@@
 
-Whereas the limiting cost underwhich a path would be considered was the sum of
+Whereas the limiting cost under which a path would be considered was the sum of
 the costs of all connections in the McAulay-Quatieri method, for the LP method
-we define the cost $\Delta_{\text{LP}}$ as the limiting cost underwhich the
+we define the cost $\Delta_{\text{LP}}$ as the limiting cost under which the
 connection between two nodes will be considered.
@@
 
-Figure~\ref{plot:mq_lp_compare_chirp_20},~\ref{plot:mq_lp_compare_chirp_15},%
-~and~\ref{plot:mq_lp_compare_chirp_10}
-show discovered partial trajectories for signals with a SNR of 20, 15, and 10
-dB,
-respectively. It is seen that while the greedy method begins to perform poorly
-at a SNR of 15dB, the LP method still gives plausible partial trajectories for
-SNRs of 10 and 15 dB. At lower SNRs, the LP formulation gives
-some paths that do not correspond to an underlying partial. These could be filtered
-out by examining the cost of these paths and comparing them to the costs of the
-others. Those that deviate from a mean cost more than a certain amount should be
-rejected. This is the strategy used in Chapter~\ref{chap:decaysep} and
-illustrated in Figure~\ref{plot:acgtra3xylofs4costlengththresh}. In any case,
-the lower SNRs are relatively challenging for any partial tracking technique.
-
-But why did the LP discover a path not present in the underlying signal? This is
-due to the cost function, which finds a path with minimum prediction error in
-using the frequency and frequency slope coefficients of one node to predict
-another node's frequency coefficient. When there are many nodes in the original
-analysis it is not surprising that some unexpected path exists.  An attribute of
-these erroneous paths is that they are not smooth. To deter the algorithm from
-finding such paths, regularization could be used like in
-Section~\ref{sec:mqfmfromphase} that minimizes the integral of the squared
-estimate of the path's second derivative. More on regularization in optimization
-can be found in \cite[ch.~6.3]{boyd2004convex}.
+Figure~\ref{plot:mq_lp_compare_chirp_10}
+shows discovered partial trajectories for signals with a SNR of 10
+dB. It is seen that while the greedy method performs poorly
+at a SNR of 10dB, the LP method still gives plausible partial trajectories.
 
@@
 
-There are problems with the proposed approach. As discussed in
-\ref{sec:lppathsearch}, ``jagged'' paths should be removed using regularization.
+There are problems with the proposed approach. Perhaps ``jagged'' paths should be removed using regularization.
 There are also situations where it is undesirable to have paths extend
@@
 as strings or bars, exhibit a spectrum where the upper partials decay more
-quickly than the lower ones (e.g., see Figure~\ref{plot:acgtra3specgram}) --- it
+quickly than the lower ones --- it
 would be desirable in these situations to have shorter paths for the upper
@@
 The proposed algorithm, while faster than algorithms based on the Viterbi
-algorithm, is still not fast. Assuming the same cost function
-$\mathcal{D}_{\text{pr.}}$ as in Section~\ref{sec:mq_lp_compare_chirp} it would
-be more efficient to consider narrow bands over which to search for paths when
-analysing signals with little frequency modulation. However, as we will see in
-Chapter~\ref{chap:amfmsep}, with different cost functions, the algorithm is
-useful for solving general $L$ shortest paths problems outside of partial
-tracking.
+algorithm, is still not fast. In many situations where computational resources are
+limited, a McAulay-Quatieri method search over many sets of small $K$ works
+sufficiently well. However in high amounts of noise the algorithm proposed here
+is robust and of tractable complexity.
 
-\section{ACKNOWLEDGMENT}
+%\section{ACKNOWLEDGMENT}
 

### 2017-04-21 bestpathslp.py

@@ -8,7 +8,7 @@ from numpy import linalg
 import sigmod as sm
 import ddm
 
-def get_lp_mats(i_frames,i_vals,dfunc,dmax,L):
+def get_lp_mats(i_frames,i_vals,dfunc,dmax,L,build_mats=True):
 
     """
     i_frames:
@@ -75,45 +75,52 @@ def get_lp_mats(i_frames,i_vals,dfunc,dmax,L):
     # i_costs is cost vector of LP
     c=np.array(i_costs)
 
-    # number of incoming connections constraints
-    r_p=sum([len(i_f) for i_f in i_frames[1:]])
-    Ap=np.ndarray((r_p,len(i_pairs)))
-    for r, i_p in enumerate(reduce(lambda x,y : x+y, i_frames[1:])):
-        Ap[r,:]=[1. if x[1]==i_p else 0. for x in i_pairs]
-    bp=np.ones((r_p,1))
+    if (build_mats):
 
-    # number of outgoing connections constraints
-    r_s=sum([len(i_f) for i_f in i_frames[:-1]])
-    As=np.ndarray((r_s,len(i_pairs)))
-    for r, i_s in enumerate(reduce(lambda x,y : x+y, i_frames[:-1] )):
-        As[r,:]=[1. if x[0]==i_s else 0. for x in i_pairs]
-    bs=np.ones((r_s,1))
+        # number of incoming connections constraints
+        r_p=sum([len(i_f) for i_f in i_frames[1:]])
+        Ap=np.ndarray((r_p,len(i_pairs)))
+        for r, i_p in enumerate(reduce(lambda x,y : x+y, i_frames[1:])):
+            Ap[r,:]=[1. if x[1]==i_p else 0. for x in i_pairs]
+        bp=np.ones((r_p,1))
 
-    # balanced number of incoming and outgoing connections for inner frames
-    r_b=sum([len(i_f) for i_f in i_frames[1:-1]])
-    Ab=Ap[:-len(i_frames[-1]),:]-As[len(i_frames[0]):,:]
-    bb=np.zeros((r_b,1))
+        # number of outgoing connections constraints
+        r_s=sum([len(i_f) for i_f in i_frames[:-1]])
+        As=np.ndarray((r_s,len(i_pairs)))
+        for r, i_s in enumerate(reduce(lambda x,y : x+y, i_frames[:-1] )):
+            As[r,:]=[1. if x[0]==i_s else 0. for x in i_pairs]
[…]

### 2017-04-21 test/bestpathslp_dp_mq_test.py

@@ -1,5 +1,6 @@
 # Try doubling up some points in the middle to see if this makes enough
 # room for all the paths
+# compare with MQ algorithm
 import matplotlib.pyplot as plt
 import numpy as np
 import bestpathslp as bplp
@@ -30,6 +31,9 @@ a=bplp.estimate_ddm_decomp(x,
 # Number of paths L
 L=6
 
+# make colours
+cmap=plt.get_cmap('magma')
+
 # Boundaries on frequencies to consider
 f_min=250.
 f_max=2250
@@ -43,7 +47,7 @@ a_flt=[]
 for a_ in a:
     a_flt.append(filter(_dp_filt,a_))
 
-fig,ax1=plt.subplots(1,1)
+fig,(ax1,ax2)=plt.subplots(1,2)
 h=0
 for a_ in a_flt:
     for a__ in a_:
@@ -52,23 +56,10 @@ for a_ in a_flt:
         t0_=h/H#float(Fs)
         t1_=(h+H)/H#float(Fs)
         ax1.plot([t0_,t1_],[f0_,f1_],c='LightGrey')
+        ax2.plot([t0_,t1_],[f0_,f1_],c='LightGrey')
     h+=H
 
-# frames in which to double the points
-i_double=range(22,34)
-
-# double the points to have overlapping paths
-for i in i_double:
-    atlen=len(a_flt[i])
-    for j in xrange(atlen):
-        a_flt[i].append(a_flt[i][j].copy())
-
-ndp=sum([len(x) for x in a_flt])
-print 'number of data points %d' % (ndp,)
-print 'average number per frame %d' % (ndp/len(a_flt),)
-print 'number of frames %d' % (len(a_flt),)
-
-# Do partial tracking
+# Do partial tracking (LP)
 # reduce lists into one big list
 i_vals=reduce(lambda x,y : x+y,a_flt)
 # produce indices for each frame
@@ -86,18 +77,67 @@ for a_ in a_flt:
     del i_frames_[:len(a_)]
 
 def dfunc(a,b):
-#    f0=np.imag(a[1])/(2.*np.pi)*Fs
-#    f1_pr=f0+(np.imag(a[1])+2.*np.imag(a[2])*H)/(2.*np.pi)*Fs
-#    f1=np.imag(b[1])/(2.*np.pi)*Fs
-#    return abs(f1_pr - f1) + np.random.uniform()*1e-3
[…]

### 2017-04-21 test/bplp_dp_mq_reg.py

@@ -1,0 +1,218 @@
+# Try doubling up some points in the middle to see if this makes enough
+# room for all the paths
+# compare with MQ algorithm
+# Regularize cost functions
+import matplotlib.pyplot as plt
+import numpy as np
+import bestpathslp as bplp
+import cvxopt
+import sys
+
+show_plot=True
+
+#fname='/Users/mondaugen/Documents/sound/timit/TIMIT/TEST/DR1/FAKS0/SA1_your_dark.f64'
+fname='sounds/chirps.f64'
+x=np.fromfile(fname,dtype='float64')
+sigpow=np.sum(x*x)/len(x)
+SNR=-0
+noisepow=sigpow*np.power(10.,SNR/10.)
+# add noise
+x+=np.random.standard_normal(len(x))*np.sqrt(noisepow)
+x=x[:len(x)]
+Fs=16000
+H=512
+M=2048
+a=bplp.estimate_ddm_decomp(x,
+        M=M,
+        H=H,
+        th_ddm=10.**(-100./20),
+        b_ddm_hz=100.,
+        o_ddm_hz=50.,
+        Fs=Fs)
+
+# Number of paths L
+L=6
+
+# make colours
+cmap=plt.get_cmap('magma')
+
+# Boundaries on frequencies to consider
+f_min=250.
+f_max=2250
+# Keep only data-points within bounds
+def _dp_filt(_a):
+    f0_=np.imag(_a[1])/(2.*np.pi)*Fs
+    f1_=(np.imag(_a[1])+2.*np.imag(_a[2])*H)/(2.*np.pi)*Fs
+    return ((max(f0_,f1_) < f_max)
+        and (min(f0_,f1_) > f_min))
+a_flt=[]
+for a_ in a:
+    a_flt.append(filter(_dp_filt,a_))
+
+fig,(ax1,ax2)=plt.subplots(1,2)
+h=0
+for a_ in a_flt:
+    for a__ in a_:
+        f0_=np.imag(a__[1])/(2.*np.pi)*Fs
+        f1_=(np.imag(a__[1])+2.*np.imag(a__[2])*H)/(2.*np.pi)*Fs
+        t0_=h/H#float(Fs)
+        t1_=(h+H)/H#float(Fs)
+        ax1.plot([t0_,t1_],[f0_,f1_],c='LightGrey')
+        ax2.plot([t0_,t1_],[f0_,f1_],c='LightGrey')
+    h+=H
+
+# Do partial tracking (LP)
[…]

### 2017-04-21 test/bplp_dp_mq_simple.py

@@ -1,0 +1,160 @@
+# compare with MQ algorithm
+# try in different SNRs to see performance
+import matplotlib.pyplot as plt
+import numpy as np
+import bestpathslp as bplp
+import cvxopt
+
+show_plot=True
+
+#fname='/Users/mondaugen/Documents/sound/timit/TIMIT/TEST/DR1/FAKS0/SA1_your_dark.f64'
+fname='sounds/chirps_simple.f64'
+SNRs=[0,6,12,18]
+fig,axs=plt.subplots(4,3,sharex=True,sharey=True)
+for SNR,axr in zip(SNRs,axs):
+    ax1=axr[1]
+    ax2=axr[2]
+    ax3=axr[0]
+    x=np.fromfile(fname,dtype='float64')
+    sigpow=np.sum(x*x)/len(x)
+    noisepow=sigpow*np.power(10.,SNR/10.)
+    # add noise
+    x+=np.random.standard_normal(len(x))*np.sqrt(noisepow)
+    x=x[:len(x)]
+    Fs=16000
+    H=512
+    M=2048
+    a=bplp.estimate_ddm_decomp(x,
+            M=M,
+            H=H,
+            th_ddm=10.**(-60./20),
+            b_ddm_hz=100.,
+            o_ddm_hz=50.,
+            Fs=Fs)
+
+    # Number of paths L
+    L=3
+
+    # make colours
+    cmap=plt.get_cmap('magma')
+
+    # Boundaries on frequencies to consider
+    f_min=250.
+    f_max=2000
+    # Keep only data-points within bounds
+    def _dp_filt(_a):
+        f0_=np.imag(_a[1])/(2.*np.pi)*Fs
+        f1_=(np.imag(_a[1])+2.*np.imag(_a[2])*H)/(2.*np.pi)*Fs
+        return ((max(f0_,f1_) < f_max)
+            and (min(f0_,f1_) > f_min))
+    a_flt=[]
+    for a_ in a:
+        a_flt.append(filter(_dp_filt,a_))
+
+    h=0
+    for a_ in a_flt:
+        for a__ in a_:
+            f0_=np.imag(a__[1])/(2.*np.pi)*Fs
+            f1_=(np.imag(a__[1])+2.*np.imag(a__[2])*H)/(2.*np.pi)*Fs
+            t0_=h/H#float(Fs)
+            t1_=(h+H)/H#float(Fs)
[…]

### 2017-04-21 test/make_chrips_simple.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+sox -n -r 16000 -c 1 -t f64 sounds/chirps_simple.f64 synth 1 \
+sine 500-600   \
+sine 1000-1200 \
+sine 1500-1800 \
+#sine 2000-2400 \
+#sine 2500-3000 \
+#sine 3000-3600 \

### 2017-04-24 paper/paper.tex
Improved plots, wrote about example in paper.

@@
 We compare the greedy and LP based methods for peak matching on a synthetic
-signal. The signal is composed of $Q=6$ chirps of constant amplitude, the $q$th
+signal. The signal is composed of $Q=3$ chirps of constant amplitude, the $q$th
 chirp $s$ at sample $n$ described by the equation
@@
 \]
-The parameters for the 6 chirps are presented in
+The parameters for the $Q$ chirps are presented in
 Table~\ref{tab:ptrackexamplechirpparams}.
@@
 
-Two 1 second long signals are synthesized at a sampling rate of 16000 Hz, the
-first with chirps 0--2, the second with chirps 3--5. We add
+A 1 second long signal is synthesized at a sampling rate of 16000 Hz, the
+chirps ramping from their initial to final frequency in that time. We add
 Gaussian distributed white noise at several SNRs to evaluate the technique in the
@@
 
-%\begin{figure}[!t]
-%    %\centering
-%    \centering
-%    \includegraphics[width=\figwidthscale\textwidth]{plots/mq_lp_compare_chirp_20.eps}
-%    \CaptionWithTitle{%
-%        \input{plots/mq_lp_compare_chirp_20.txt}%
-%    }{ Line-segments representing the frequency and frequency-slope at local
-%        spectrogram maxima. In the bottom two plots the line segments not deemed
-%        by the respective algorithms as belonging to a partial path are
-%        discarded, revealing the estimated partial trajectories. See
-%        Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
-%    \label{plot:mq_lp_compare_chirp_20}}
-%\end{figure}
-%\begin{figure}[!t]
-%    %\centering
-%    \centering
-%    \includegraphics[width=\figwidthscale\textwidth]{plots/mq_lp_compare_chirp_15.eps}
-%    \CaptionWithTitle{%
-%        \input{plots/mq_lp_compare_chirp_15.txt}%
-%    }{ Line-segments representing the frequency and frequency-slope at local
-%        spectrogram maxima. In the bottom two plots the line segments not deemed
-%        by the respective algorithms as belonging to a partial path are
-%        discarded, revealing the estimated partial trajectories. See
-%        Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
-%    \label{plot:mq_lp_compare_chirp_15}}
-%\end{figure}
-\begin{figure}[!t]
+\begin{figure*}
     %\centering
     \centering
-    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/mq_lp_compare_chirp_10.eps}}
-    \CaptionWithTitle{%
-        \input{plots/mq_lp_compare_chirp_10.txt}%
-    }{ Line-segments representing the frequency and frequency-slope at local
-        spectrogram maxima. In the bottom two plots the line segments not deemed
-        by the respective algorithms as belonging to a partial path are
-        discarded, revealing the estimated partial trajectories. See
-        Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
-    \label{plot:mq_lp_compare_chirp_10}}
-\end{figure}
+    \centerline{\includegraphics[width=0.75\textwidth]{plots/mq_lp_compare_chirps.eps}}
+    { Line-segments representing the frequency and frequency-slope at local
+        spectrogram maxima. The coloured segments correspond to connected paths
+        returned by the search algorithms. Plots 1--3.a. show the atomic
+        decomposition of the signal before partial tracking for SNRs of 0, -6
+        and -12 dB, respectively. Plots 1--3.b. show the partial paths
+        discovered by the LP method and plots 1--3.c. show the paths discovered
+        by the McAulay-Quatieri method. 
+        See Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
+    \label{plot:mq_lp_compare_chirps}}
+\end{figure*}
 
-A spectrogram of each signal is computed with an analysis window length of 1024
-samples and a hop-size $H$ of 256 samples. Local maxima are searched in 150 Hz
-wide bands spaced 75 Hz apart. A local maximum is only accepted if its amplitude
-is greater than -20 dB. The bin corresponding to each local maximum and its two
+A spectrogram of each signal is computed with an analysis window length of 2048
+samples and a hop-size $H$ of 512 samples. Local maxima are searched in 100 Hz
+wide bands spaced 50 Hz apart. The bin corresponding to each local maximum and its two
 surrounding bins are used by the Distribution Derivative Method
-(DDM) to estimate the
+(DDM) \cite{betser2009sinusoidal} to estimate the
 local chirp parameters, the $i$th set of parameters in frame $k$ denoted
@@
 \right\}$ (the atoms used by the DDM are generated from 4-term continuous
-Nuttall windows). The results of the analyses of both signals are lumped together and
-it is on this lumped data that we perform partial tracking.
+Nuttall windows \cite{nuttall1981some}). Partial tracking is performed on the
+resulting atomic decomposition.
 
@@
 parameters in frame $k$. For the greedy method, the search for partial paths is
-restricted to one frame ahead like in \cite{mcaulay1986speech}, otherwise the
+restricted to two frames ahead, i.e., paths of length $K_{\text{MQ}}=3$ are sought, otherwise the
 computation becomes intractable. For the LP
-method, to keep the computation time reasonable, we search over 6 frames for 6
-best paths (the number of paths does not affect the computation time).
-To maintain connected paths, the search on the next frames uses the end nodes of
-the last search as starting points. For both methods, the search is restricted
-to nodes between frequencies 250 to 2250 Hz.
+method the search is carried out over all frames ($K_{\text{LP}}=28$). %TODO: Is it?
+The cost thresholding values are ${\Delta_{\text{MQ}} = \Delta_{\text{LP}} =
+0.1}$. For both methods, the search is restricted
+to nodes between frequencies 250 to 2000 Hz.
 
-Figure~\ref{plot:mq_lp_compare_chirp_10}
-shows discovered partial trajectories for signals with a SNR of 10
-dB. It is seen that while the greedy method performs poorly
-at a SNR of 10dB, the LP method still gives plausible partial trajectories.
+Figure~\ref{plot:mq_lp_compare_chirps}
+shows discovered partial trajectories for signals at various SNRs. It is seen
+that while the greedy method starts performing poorly at an SNR of -6db, the LP method
+still gives plausible partial trajectories. The LP method returns paths spanning
+all $K$ frames, due to the constraints. The McAulay-Quatieri method in general does not,
+but longer paths can be formed in a straightforward way after the initial short path
+search step \cite{mcaulay1986speech}.
+
+It is interesting to note that the paths are found by only considering the
+prediction error of the initial frequency of the atom. Other cost functions can
+be chosen depending on the nature of the signal: reasonable cost functions here
+might be similarity of the atoms's energies or frequency slopes.
 
@@
 
-There are problems with the proposed approach. Perhaps ``jagged'' paths should be removed using regularization.
-There are also situations where it is undesirable to have paths extend
+There are problems with the proposed approach. 
+There are situations where it is undesirable to have paths extend
 throughout the entire lattice. Acoustic signals produced by striking media, such
 as strings or bars, exhibit a spectrum where the upper partials decay more
-quickly than the lower ones --- it
-would be desirable in these situations to have shorter paths for the upper
-partials, those decaying more quickly. This could be addressed as in
+quickly than the lower ones; it
+would be desirable in these situations to have shorter paths for these
+partials. This could be addressed as in
 \cite{depalle1993tracking} where the signal is divided into overlapping sequences of
@@
 The proposed algorithm, while faster than algorithms based on the Viterbi
-algorithm, is still not fast. In many situations where computational resources are
+algorithm \cite{wolf1989finding}, is still not fast. In many situations where computational resources are
 limited, a McAulay-Quatieri method search over many sets of small $K$ works
 sufficiently well. However in high amounts of noise the algorithm proposed here
-is robust and of tractable complexity.
+is robust while still of tractable complexity.
 

### 2017-04-24 test/bplp_dp_mq_simple.py

@@ -4,43 +4,63 @@ import matplotlib.pyplot as plt
 import numpy as np
 import bestpathslp as bplp
 import cvxopt
+import ddm
 
-show_plot=True
+plt.rc('text',usetex=True)
+plt.rc('font',**ddm.FONT_OPT['dafx'])
+
+show_plot=False
 
 #fname='/Users/mondaugen/Documents/sound/timit/TIMIT/TEST/DR1/FAKS0/SA1_your_dark.f64'
 fname='sounds/chirps_simple.f64'
-SNRs=[0,6,12,18]
-fig,axs=plt.subplots(4,3,sharex=True,sharey=True)
-for SNR,axr in zip(SNRs,axs):
+# minimum power of atom to consider
+minpow=-60
+SNRs=[0,-6,-12]
+fig,axs=plt.subplots(3,len(SNRs),sharex=True,sharey=True)
+# Boundaries on frequencies to consider
+f_min=250.
+f_max=2000
+Fs=16000
+H=512
+M=2048
+y=np.fromfile(fname,dtype='float64')
+sigpow=np.sum(y*y)/len(y)
+print 'sigpow: %f' % (np.log(sigpow)/np.log(10)*10,)
+t_min=0.
+t_max=(((len(y)-M)/H)*H)/float(Fs)
+# make colours
+cmap=plt.get_cmap('magma')
+cmapgrey=plt.get_cmap('gray')
+for SNR,axr,ax_i in zip(SNRs,axs.T,xrange(axs.shape[1])):
     ax1=axr[1]
     ax2=axr[2]
     ax3=axr[0]
-    x=np.fromfile(fname,dtype='float64')
-    sigpow=np.sum(x*x)/len(x)
-    noisepow=sigpow*np.power(10.,SNR/10.)
+
+    for i,a in enumerate(['a','b','c']):
+        axr[i].set_title('%d.%s.' % (ax_i+1,a))
+        axr[i].locator_params(nbins=5)
+
+    noisepow=sigpow*np.power(10.,-SNR/10.)
+    print 'noisepow: %f' % (np.log(noisepow)/np.log(10)*10,)
     # add noise
-    x+=np.random.standard_normal(len(x))*np.sqrt(noisepow)
+    x=y+np.random.standard_normal(len(y))*np.sqrt(noisepow)
+    totpow=np.sum(x*x)/len(x)
+    print 'totpow: %f' % (np.log(totpow)/np.log(10)*10,)
[…]

### 2017-04-25 paper/paper.tex
Added introduction. Need to add 'further work' to conclusion.

@@
 
-\section{Partial Tracking\label{chap:partialtracking}}
+\section{Introduction}
 
-%In the previous paper, we saw how to estimate parameters of sinusoids with
-%polynomial phase. While theoretically applicable to signals of arbitrary length,
-%for reasons of flexibility and efficiency, we usually estimate the local
-%parameters of the signal under a low-order model and connect multiple
-%estimations to form a partial. We will call these local estimations ``analysis
-%points'' or ``parameter sets''.
+Atomic decompositions of audio allow for the discovery of meaningful underlying
+structures such as musical notes \cite{gribonval2003harmonic} or sparse
+representations \cite{plumbley2010sparse}. A classical structure sought in
+decompositions of speech and music signals is the sum-of-sinusoids model: windowed sinusoidal atoms in the
+decomposition of sufficient energy and in close proximity in both time and
+frequency are considered as \textit{connected}. The progressions of these
+connected atoms in time form paths or \textit{partial trajectories}.
 
-This paper presents an interpretation of the \textit{peak matching} procedure
-of McAulay and Quatieri \cite{mcaulay1986speech}, a classical approach to discovering partials. Our
-interpretation allows for the specification of an arbitrary cost function
-measuring the plausibility that a set of analysis points forms the path of a
-partial. With this path interpretation, we were able to design a technique that finds the
-optimal set of paths under a constraint on the number of paths. The paper 
-concludes with an example of partial tracking on a synthetic signal.
+Many authors have considered the partial tracking problem, beginning with
+\cite{mcaulay1986speech}. Their technique is improved upon
+in \cite{lagrange2003enhanced} with the use of linear prediction to improve the
+plausibility of partial tracks. Rather than seeking individual paths, in
+\cite{depalle1993tracking} the most plausible sequence of connections and
+detachments between atoms is determined via an extension of the Viterbi
+algorithm proposed in \cite{wolf1989finding}. Improvements to this technique are
+made in \cite{kereliuk2008improved} by incorporating the frequency slope into
+atom proximity evaluations.
 
-Typically the discrete time short-time Fourier transform (DTSTFT) is computed
-for a block of contiguous samples, called a \textit{frame} and these frames are
+The latter techniques seeking globally optimal sets of paths incur great
+computational cost due to the large number of possible solutions. For this reason, in
+this paper we propose a linear programming \textit{relaxation}-formulation of
+the optimal path-set problem based on
+an algorithm for the tracking of multiple objects in video
+\cite{jiang2007linear}. It will be shown that this algorithm has favourable
+asymptotic complexity and performs well on the tracking of chirps in high levels
+of noise.
+
+\subsection{Note on notation}
+
+The atomic decompositions used in this paper consider blocks of 
+of contiguous samples, called \textit{frames} and these frames are
 computed every $H$ samples, $H$ being the \textit{hop-size}. We will denote the
-$N_{k}$ sets of parameters at local maxima in frame $k$ as $\theta_0^{k},
+$N_{k}$ sets of parameters for atoms found in the decomposition in frame $k$ as $\theta_0^{k},
 \dotsc, \theta_{N_{k}-1}^{k}$ and the $N_{k+1}$ in frame $k+1$ as
 $\theta_0^{k+1}, \dotsc, \theta_{N_{k+1}-1}^{k+1}$ where $k$ and $k+1$ refer to
-adjacent frames. We are interested in paths that extend across $K$ frames where
+adjacent frames.
+
+The total number of nodes is $M = \sum_{k=0}^{K-1} N_{k}$. $\theta_{i}^{j}$ is the
+$i$th node of the $j$th frame, $\theta^{j}$ the set of all the nodes in the
+$j$th frame and $\theta_{m}$ the $m$th node out of all $M$ nodes ($0 \leq m <
+M$).
+
+We are interested in paths that extend across $K$ frames where
 each path touches only one parameter set and each parameter set is either
 exclusive to a single path or is not on a path.
-
-\subsection{Note on notation}
 
@@
 the pair and $a_{1}$ the second.
-
-The number of frames is denoted $K$, the number of nodes in the $k$th frame $N_k$ and
-the total number of nodes $M = \sum_{k=0}^{K-1} N_{k}$. $\theta_{i}^{j}$ is the
-$i$th node of the $j$th frame, $\theta^{j}$ the set of all the nodes in the
-$j$th frame and $\theta_{m}$ the $m$th node out of all $M$ nodes ($0 \leq m <
-M$).
-
-%In Section~\ref{sec:mqfmfromphase} we discussed how to determine reasonable
-%values for the coefficients of a cubic phase polynomial by using the frequency,
-%phase and time difference of two local maxima in the DTSTFT. In this section we
-%discuss possible ways of determining which local maxima are connected. This is
-%referred to as \textit{peak matching} \cite{mcaulay1986speech}
-%or \textit{partial tracking} \cite{smith1987parshl} \cite{depalle1993tracking}.
 
@@
 
-In \cite[q.~748]{mcaulay1986speech} the peak matching algorithm is described in
+In \cite[p.~748]{mcaulay1986speech} the peak matching algorithm is described in
 a number of steps; we summarize them here in a way comparable with the linear
@@
 will allow for arbitrary parameter sets $\theta$.  Define a distance function
-$\mathcal{D}
-\left( \theta_{i},\theta_{j} \right)$ that computes the
+$\mathcal{D} \left( \theta_{i},\theta_{j} \right)$ that computes the
 similarity between $2$ sets of parameters. We will now consider a method that
@@
 in the their respective dimensions from consideration
-and continue until $L$ tuples have been determined or the distances exceed some
-threshold $\Delta_{\text{MQ}}$. This is summarized in Algorithms~\ref{alg:mq_peak_match}
+and continue until $L$ tuples have been determined or a distance between a pair
+of nodes on the path
+exceeds some
+threshold $\Delta_{\text{MQ}}$. This is summarized in
+Algorithm~\ref{alg:mq_peak_match}.
 
@@
             \BS{C}$\;
-            \If{$ C_{\Gamma_{l}} > \Delta_{\text{MQ}}$}{
+            \If{$ \exists i,j \in \Gamma_{l} : 
+            \mathcal{D} \left( \theta_{i},\theta_{j} \right) > \Delta_{\text{MQ}}$}{
             \KwRet{$\Gamma$}
@@
 $K$. Nevertheless, the method is simple to implement, computationally negligible
-when $K$ is small, and works well with audio signals \cite{mcaulay1986speech}
+when $K$ is small, and works well with a variety of audio signals such as speech
+\cite{mcaulay1986speech} and music
 \cite{smith1987parshl}.
@@
 
-Whereas the limiting cost under which a path would be considered was the sum of
-the costs of all connections in the McAulay-Quatieri method, for the LP method
+Similar to the McAulay-Quatieri method 
 we define the cost $\Delta_{\text{LP}}$ as the limiting cost under which the
-connection between two nodes will be considered.
+connection between two nodes will be considered in the LP method.
 
@@
 
-\begin{figure*}
+\begin{figure*}[!t]
     %\centering
@@
     \centerline{\includegraphics[width=0.75\textwidth]{plots/mq_lp_compare_chirps.eps}}
-    { Line-segments representing the frequency and frequency-slope at local
-        spectrogram maxima. The coloured segments correspond to connected paths
-        returned by the search algorithms. Plots 1--3.a. show the atomic
-        decomposition of the signal before partial tracking for SNRs of 0, -6
-        and -12 dB, respectively. Plots 1--3.b. show the partial paths
-        discovered by the LP method and plots 1--3.c. show the paths discovered
-        by the McAulay-Quatieri method. 
-        See Table~\ref{tab:ptrackexamplechirpparams} for the chirp parameters.
-    \label{plot:mq_lp_compare_chirps}}
+    \caption{ Line-segments representing the frequency and frequency-slope at
+        local spectrogram maxima. The power of each atom is represented by
+        shades of grey: black atoms have the highest power and white the lowest.
+        The coloured segments correspond to connected paths returned by the
+        search algorithms. Plots 1--3.a. show the atomic decomposition of the
+        signal before partial tracking for SNRs of 0, -6 and -12 dB,
+        respectively.  Plots 1--3.b. show the partial paths discovered by the LP
+        method and plots 1--3.c. show the paths discovered by the
+        McAulay-Quatieri method.  See Table~\ref{tab:ptrackexamplechirpparams}
+        for the chirp parameters.  \label{plot:mq_lp_compare_chirps}
+    }
 \end{figure*}
@@
 $\theta_{i}^{k} = \left\{ \phi_{i}^{k} , \omega_{i}^{k} , \psi_{i}^{k}
-\right\}$ (the atoms used by the DDM are generated from 4-term continuous
-Nuttall windows \cite{nuttall1981some}). Partial tracking is performed on the
+\right\}$ (the atoms used by the DDM are generated from 4-term
+once-differentiable Nuttall windows \cite{nuttall1981some}). Partial tracking is performed on the
 resulting atomic decomposition.
@@
 shortest paths in a lattice. An algorithm was then proposed minimizing the sum
-of the $L$ paths, using a linear programming approach. It was shown on synthetic
-signals that the new approach finds plausible paths in lattices with a
-large number of spurious nodes.
+of the $L$ paths, using a linear programming approach. The complexity of the new
+algorithm was shown to be generally less than the Viterbi-based algorithms and
+the McAulay-Quatieri algorithm for large $K$.
+It was shown on synthetic signals that the new approach finds plausible paths in
+lattices with a large number of spurious nodes.
 
-There are problems with the proposed approach. 
+The proposed approach has some drawbacks.
 There are situations where it is undesirable to have paths extend
@@
 
-The proposed algorithm, while faster than algorithms based on the Viterbi
-algorithm \cite{wolf1989finding}, is still not fast. In many situations where computational resources are
-limited, a McAulay-Quatieri method search over many sets of small $K$ works
+The proposed algorithm, while asymptotically faster than other partial tracking
+algorithms, is still not fast. In many situations where computational resources
+are limited, a McAulay-Quatieri method search over many sets of small $K$ works
 sufficiently well. However in high amounts of noise the algorithm proposed here
 is robust while still of tractable complexity.
+
+%TODO: Improvements and extensions
 

### 2017-04-25 paper/paper.tex
Added conclusion and did one read-through.

@@
     \cite{mcaulay1986speech} is greedy and exhibits exponential complexity for
-    long searches. A linear programming (LP) formulation to find the best $L$ paths
-    in a lattice is described and its complexity is analysed. Finally it is
-    demonstrated that the new LP formulation outperforms the classical algorithm
-    in the tracking of sinusoidal chirps in high levels of noise --- both in
-    computational complexity and robustness.
+    long searches, while approaches based on the Viterbi algorithm exhibit
+    factorial complexity \cite{depalle1993tracking} \cite{wolf1989finding}. A
+    linear programming (LP) formulation to find the best $L$ paths in a lattice
+    is described and its complexity is shown to be less than previous
+    approaches. Finally it is demonstrated that the new LP formulation
+    outperforms the classical algorithm in the tracking of sinusoidal chirps in
+    high levels of noise.
 \end{abstract}
@@
 \begin{keywords}
-partial tracking, linear programming, optimization, additive synthesis
+partial tracking, linear programming, optimization, additive synthesis, atomic
+decomposition, regularized approximation
 \end{keywords}
@@
 computational cost due to the large number of possible solutions. For this reason, in
-this paper we propose a linear programming \textit{relaxation}-formulation of
+this paper we propose a linear programming \textit{relaxation} formulation of
 the optimal path-set problem based on
@@
 In this section, we present the McAulay-Quatieri method of peak matching. It is
-conceptually simple and a set of short paths can be computed quickly, but
-it can be sensitive to spurious peaks and is optimal only in the sense that
-the set of paths computed contains the best path possible --- the quality of the
-other paths may be compromised under this criterion.
+conceptually simple and a set of short paths can be computed quickly, but it can
+be sensitive to spurious peaks and its complexity becomes unwieldly for long
+searches.
 
@@
 programming formulation to be presented shortly. In that paper, the parameters
-of each data point are the instantaneous amplitude, phase, and frequency but we
-will allow for arbitrary parameter sets $\theta$.  Define a distance function
-$\mathcal{D} \left( \theta_{i},\theta_{j} \right)$ that computes the
-similarity between $2$ sets of parameters. We will now consider a method that
-finds $L$ tuples of parameters that are closest.
+of each data point are the instantaneous amplitude, phase, and frequency but
+here we allow for arbitrary parameter sets $\theta$.  Define a distance function
+$\mathcal{D} \left( \theta_{i},\theta_{j} \right)$ that computes the similarity
+between $2$ sets of parameters. We will now consider a method that finds $L$
+tuples of parameters that are closest.
 
@@
 otherwise no connections, a constraint that can be enforced through the
-following linear inequality. Define $\BS{A}^{\text{I}} \in
+following linear inequality: define $\BS{A}^{\text{I}} \in
 \mathbb{R}^{R_{\text{I}} \times P}$ with $R_{\text{I}} = \sum_{k=1}^{K-1}
@@
 
-To ensure no breaks in the paths it is required that the number of incoming
+To forbid breaks in the paths it is required that the number of incoming
 connections into a given node equal the number of outgoing connections for the
@@
 \end{equation}
-where $\BS{I}$ is the identity matrix.
+where $\BS{I}$ is the identity matrix. A proof that the solution
+$\boldsymbol{x}^{\ast}$ will have entries equal to either $0$ or $1$ can be
+found in \cite[p.~167]{parker1988discrete}.
 
@@
 Although the matrices involved in (\ref{eq:lpprogfull}) are large, only a small
-fraction of their values are non-zero. As stated above, the number of variables in $\BS{x}$ is
-$P = (K-1)N^{2}$. Even though matrices $\BS{A}^{\text{I}}, \BS{A}^{\text{O}} \in
-\mathbb{R}^{N(K-1) \times P}$, each contains only $P$ non-zero
-entries.  $\BS{A}^{\text{B}} \in \mathbb{R}^{N(K-1) \times P}$ but contains only
-$2N^{2}(K-2)$ non-zero entries while $\BS{A}^{\text{C}}_{K-2} \in \mathbb{R}^{P}$
-contains merely $N$. The $\BS{x} \geq \BS{0}$ constraint requires a matrix
-with $P$ non-zero entries. The total memory complexity is therefore $4P +
-2N^{2}(K-2)$ floating-point numbers.
+fraction of their values are non-zero. Matrices $\BS{A}^{\text{I}},
+\BS{A}^{\text{O}} \in \mathbb{R}^{N(K-1) \times P}$, but each contains only $P$
+non-zero entries.  Furthermore $\BS{A}^{\text{B}} \in \mathbb{R}^{N(K-1) \times
+P}$ but contains only $2N^{2}(K-2)$ non-zero entries while
+$\BS{A}^{\text{C}}_{K-2} \in \mathbb{R}^{P}$ contains merely $N$. The $\BS{x}
+\geq \BS{0}$ constraint requires a matrix with $P$ non-zero entries. The total
+memory complexity including the entries in $\cLP$ and the right-hand-sides of
+(\ref{eq:lpprogfull}) is $2N^{2}(K-2) + 4P + 2N(K-1) + N + 1$ non-zero
+floating-point numbers.
 
@@
 algorithms use the distance metric $\mathcal{D}_{\text{pr.}}$ between two parameters sets:
-\[
+\begin{equation}
+    \label{eq:examplecostfun}
     \mathcal{D}_{\text{pr.}} \left( \theta_{i}^{k},
@@
     \psi_{i}^{k} H - \omega_{j}^{k+1} \right)
-\]
+\end{equation}
 which is the error in predicting $j$th frequency in frame $k+1$ from the $i$th
@@
 computation becomes intractable. For the LP
-method the search is carried out over all frames ($K_{\text{LP}}=28$). %TODO: Is it?
+method the search is carried out over all frames ($K_{\text{LP}}=28$).
 The cost thresholding values are ${\Delta_{\text{MQ}} = \Delta_{\text{LP}} =
@@
 shows discovered partial trajectories for signals at various SNRs. It is seen
-that while the greedy method starts performing poorly at an SNR of -6db, the LP method
+that while the greedy method starts performing poorly at an SNR of -6 dB, the LP method
 still gives plausible partial trajectories. The LP method returns paths spanning
@@
 
-In this paper we reformulated the classical greedy algorithm of McAulay and
+In this paper we reformulated the classical partial tracking technique of McAulay and
 Quatieri and showed that it can be seen as a greedy algorithm for finding the $L$
@@
 of the $L$ paths, using a linear programming approach. The complexity of the new
-algorithm was shown to be generally less than the Viterbi-based algorithms and
+algorithm was shown to be generally less than the Viterbi-based methods and
 the McAulay-Quatieri algorithm for large $K$.
@@
 
+In its current form, the path search may choose undesirable paths if a
+convenient node is missing from the following frame. An extension could consider
+nodes some number of frames ahead.
+
 The proposed algorithm, while asymptotically faster than other partial tracking
-algorithms, is still not fast. In many situations where computational resources
+algorithms, is still not fast. In situations where computational resources
 are limited, a McAulay-Quatieri method search over many sets of small $K$ works
@@
 
-%TODO: Improvements and extensions
+It may be possible to improve the performance of the algorithm by the use of
+different cost functions and regularization. The cost function
+(\ref{eq:examplecostfun}) could be extended to encourage similarity between
+frequency slopes or amplitude information. Each metric should be scaled
+according to its desired contribution to the cost.
+
+There may also be a way to extract individual paths through the use of auxiliary
+variables in (\ref{eq:lpprogfull}). If so, path specific costs such as overall
+smoothness or fit to a particular model could be incorporated.
+
+In any case, it would be interesting to further investigate programming
+relaxations encouraging underlying discrete structures plausible for audio
+in the framework of regularized approximation. These structures are closer to
+ground-truth structures for speech (text) and music (the musical score).
 

### 2019-01-15 paper/build_paper.sh
Added conditional building of paper for Archivx
This basically just removes the header but still uses the WASPAA style.

@@ -4,9 +4,18 @@
 
 # Convert all eps files to pdf
 
-pdflatex paper.tex
+outpdf_name=Esterer_Nicholas_WASPAA_2017.pdf
+[[ $BUILD_FOR_ARCHIVX ]] && outpdf_name=Esterer_Nicholas_archivx.pdf
+
+# set BUILD_FOR_ARCHIVX=1 for formatting for Archivx
+paper_build ()
+{
+    echo '\def\buildforarchivx{'"$BUILD_FOR_ARCHIVX"'} \input{paper.tex}'
+    pdflatex '\def\buildforarchivx{'"$BUILD_FOR_ARCHIVX"'} \input{paper.tex}'
+}
+paper_build
 BIBINPUTS=. bibtex paper.aux
-pdflatex paper.tex
-pdflatex paper.tex
-mv paper.pdf Esterer_Nicholas_WASPAA_2017.pdf
+paper_build
+paper_build
+mv paper.pdf "$outpdf_name"
 #dvipdf thesis.dvi
